### 2020-09-30 paper/paper.tex
initial commit

\documentclass{article}

% We suggest
% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2020_tda}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2020_tda}

% to avoid loading the natbib package, add option nonatbib:
\usepackage[nonatbib]{neurips_2020_tda}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{booktabs}       % professional-quality tables
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{microtype}      % microtypography
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{paralist}       % in-paragraph enumerations
\usepackage{siunitx}        % SI units

\urlstyle{same}

%HANS's CONVENIENCES

\title{Sheaves, GNNs, and Pooling}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Hans Riess  \\
  Department of Electrical and Systems Engineering \\
  Universiyt of Pennsylvania\\
  Philadelphia, PA 19104 \\
  \texttt{hmr@seas.upenn.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
 To write...
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sheaves}

\section{Graph Neural Networks}

\section{Pooling}

\begin{ack}
I would like to thank...
\end{ack}

\

\end{document}

### 2020-09-30 code/convert_point_cloud.py

@@ -1,0 +1,11 @@
+import numpy as np
+
+def off_to_pointcloud(path):
+    f = open(path,'r')
+    f.readline()
+    num_vertices = int(f.readline().split()[0])
+    data_matrix = np.zeros([num_vertices,3])
+    for i in range(num_vertices):
+        x = np.array([float(t) for t in f.readline().split()])
+        data_matrix[i,:]=x
+    return data_matrix

### 2020-09-30 code/features.py

@@ -1,0 +1,30 @@
+import numpy as np
+import itertools as it
+
+def d(x,y):
+    return np.sqrt(np.dot(x-y,x-y))
+
+def distance_matrix(data_matrix):
+    N = data_matrix.shape[0]
+    D = np.zeros([N,N])
+    for (i,j) in it.product(range(N),range(N)):
+        D[i,j]= d(data_matrix[i,:],data_matrix[j,:])
+    return D
+
+def density_filtration(data_matrix,k):
+    D = distance_matrix(data_matrix)
+    N = data_matrix.shape[0]
+    dim = data_matrix.shape[1]
+    filtration_matrix = np.zeros([N,dim+1])
+    filtration_matrix[:,:dim]=data_matrix
+    for i in range(N):
+        row = data_matrix[i,:]
+        k_nearest = sorted(row,reverse=True)[:k]
+        summation = 0
+        for j,x in enumerate(k_nearest):
+            summation+=D[i,j]
+        filtration_matrix[i,dim]=summation/k
+    return filtration_matrix
+
+def curvature_filtration(data_matrix,k):
+    return None

### 2020-09-30 code/main.py

@@ -1,0 +1,42 @@
+import os
+from convert_point_cloud import off_to_pointcloud
+from features import density_filtration
+from rivet import write_rivet_input,rivet_find_invariants
+import random
+
+main_path = "C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/data/ModelNet10/ModelNet10/"
+training_data = []
+testing_data = []
+for category in os.listdir(main_path):
+    path_train = "C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/data/ModelNet10/ModelNet10/"+category+'/train/'
+    for index,filename in enumerate(os.listdir(path_train)):
+        path = path_train + filename
+        print(filename)
+        point_cloud = off_to_pointcloud(path)
+        training_data.append((point_cloud,category,index))
+    path_test = "C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/data/ModelNet10/ModelNet10/"+category+'/test/'
+    for index,filename in enumerate(os.listdir(path_test)):
+        path = path_test + filename
+        print(filename)
+        point_cloud = off_to_pointcloud(path)
+        testing_data.append((point_cloud,category,index))
+
+random.shuffle(training_data)
+random.shuffle(testing_data)
+k=100
+x_bins = 20
+y_bins = 20
+
+for (point_cloud,label,index) in training_data:
+    name = "training_point_cloud_" + str(label)+"-" + str(index)+".txt"
+    write_rivet_input(point_cloud,density_filtration,k,name)
+    for deg in range(2):
+        output_name = 'training_invariants_deg_'+str(deg)+ "_"+ str(label)+"-"+str(index)+".txt"
+        rivet_find_invariants(name,output_name,deg,x_bins,y_bins)
+
+for (point_cloud,label,index) in testing_data:
+    name = "testing_point_cloud_" + str(label)+"-"+str(index)+".txt"
+    write_rivet_input(point_cloud,density_filtration,k,name)
+    for deg in range(2):
+        output_name = 'testing_invariants_deg_'+str(deg)+ "_"+ str(label)+"-"+str(index)+".txt"
+        rivet_find_invariants(name,output_name,deg,x_bins,y_bins)

### 2020-09-30 code/puschel.py

@@ -1,0 +1,50 @@
+import numpy as np
+import numpy.random as rd
+import itertools as it
+
+def normalize_array(matrix,normalize='L1'):
+    for i,row in enumerate(matrix):
+        if normalize == 'L2':
+            matrix[i,:]=row/np.linalg.norm(row)
+        elif normalize == "L1":
+            matrix[i,:]=row/np.sum(row)
+        elif normalize == "stochastic":
+            matrix[i,:]=row/np.max(row)
+    return matrix
+
+def p_convolve(conv_filter,signal,filter_pos=(0,0)):
+    (m,n)=signal.shape
+    (m_f,n_f)=conv_filter.shape
+    (i0,j0)=filter_pos
+    output = np.zeros([m,n])
+    if m_f<m and n_f<n:
+        result = np.zeros([m,n])
+        result[i0:m_f+i0,j0:n_f+j0]=conv_filter
+        conv_filter = result
+    elif conv_filter.shape!=signal.shape:
+        print('Filter size exceeds the dimension of the signal array')
+        return None
+    for x in it.product(range(m),range(n)):
+        terms = []
+        for e in it.product(range(m),range(n)):
+            term = conv_filter[e]*signal[min(e,x)]
+            terms.append(term)
+        output[x] = np.sum(terms)
+    return output
+
+def local_max_pool(signal):
+    (m,n)=signal.shape
+    output = np.zeros([m,n])
+    for (i,j) in it.product(range(m),range(n)):
+        output[i,j]= np.max([signal[i,j],signal[min(i+1,m-1),j],signal[max(i-1,0),j],signal[i,min(j+1,m-1)],signal[i,max(j-1,0)]])
+    return output
+
+# def p_translate_convolve(conv_filter,signal):
+#     (m,n)=signal.shape
+#     (m_f,n_f)=conv_filter.shape
+#     output = np.zeros([m,n])
+#     for i0 in range(m-m_f+1):
+#         for j0 in range(n-n_f+1):
+#             output+=p_convolve(conv_filter,signal,(i0,j0))
+#     return output
+

### 2020-09-30 code/rivet.py

@@ -1,0 +1,21 @@
+import os
+
+def write_rivet_input(data_matrix,filtration_function,k,name):
+    filtration_matrix = filtration_function(data_matrix,k)
+    filtration_name = filtration_function.__name__
+    newline = "\n"
+    space = " "
+    dim = str(filtration_matrix.shape[1]-1)
+    f = open(name,"w")
+    f.write("points"+newline)
+    f.write(dim+newline)
+    f.write("[-] "+filtration_name+newline)
+    for row in filtration_matrix:
+        print(row)
+        f.write(str(row[0]) + space + str(row[1]) + space + str(row[2])+ newline)
+    return None
+
+def rivet_find_invariants(data_file_name,output_file_name, h_dim, x_bins,y_bins):
+    cmd = "./rivet_console " + data_file_name + " --betti -H "+str(h_dim) + " -x "+str(x_bins)+" -y "+str(y_bins) + " > "+output_file_name
+    os.system(cmd)
+    return None

### 2020-09-30 code/testing.py

@@ -1,0 +1,10 @@
+import numpy as np
+from features import density_filtration
+from rivet import rivet_find_invariants,write_rivet_input
+k=10
+a = np.random.rand(100,2)
+print(a)
+name = "test_point_cloud"
+output_name = "test_invariants"
+write_rivet_input(a,density_filtration,k,"test_point_cloud")
+rivet_find_invariants(name,output_name,1,10,10)

### 2020-09-30 code/training.py

@@ -1,0 +1,13 @@
+import numpy as np
+import torch
+from puschel import normalize_array,p_convolve,local_max_pool
+
+def sigmoid(x):
+    return 1/(1+np.e**(-x))
+
+def relu(x):
+    return np.maximum(np.zeros(x.shape),x)
+
+
+
+

### 2020-09-30 code/main.py
paths in main.py

@@ -4,18 +4,22 @@ from features import density_filtration
 from rivet import write_rivet_input,rivet_find_invariants
 import random
 
-main_path = "C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/data/ModelNet10/ModelNet10/"
+main_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
 training_data = []
 testing_data = []
 for category in os.listdir(main_path):
-    path_train = "C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/data/ModelNet10/ModelNet10/"+category+'/train/'
+    path_train = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"+category+'/train/'
     for index,filename in enumerate(os.listdir(path_train)):
+        if filename == ".DS_Store":
+            continue
         path = path_train + filename
         print(filename)
         point_cloud = off_to_pointcloud(path)
         training_data.append((point_cloud,category,index))
-    path_test = "C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/data/ModelNet10/ModelNet10/"+category+'/test/'
+    path_test = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"+category+'/test/'
     for index,filename in enumerate(os.listdir(path_test)):
+        if filename == ".DS_Store":
+            continue
         path = path_test + filename
         print(filename)
         point_cloud = off_to_pointcloud(path)
@@ -24,8 +28,8 @@ for category in os.listdir(main_path):
 random.shuffle(training_data)
 random.shuffle(testing_data)
 k=100
-x_bins = 20
-y_bins = 20
+x_bins = 100
+y_bins = 100
 
 for (point_cloud,label,index) in training_data:
     name = "training_point_cloud_" + str(label)+"-" + str(index)+".txt"

### 2020-09-30 code/main.py
minor

@@ -28,8 +28,8 @@ for category in os.listdir(main_path):
 random.shuffle(training_data)
 random.shuffle(testing_data)
 k=100
-x_bins = 100
-y_bins = 100
+x_bins = 10
+y_bins = 10
 
 for (point_cloud,label,index) in training_data:
     name = "training_point_cloud_" + str(label)+"-" + str(index)+".txt"

### 2020-09-30 code/rivet.py

@@ -11,7 +11,6 @@ def write_rivet_input(data_matrix,filtration_function,k,name):
     f.write(dim+newline)
     f.write("[-] "+filtration_name+newline)
     for row in filtration_matrix:
-        print(row)
         f.write(str(row[0]) + space + str(row[1]) + space + str(row[2])+ newline)
     return None
 

### 2020-10-01 code/neural.py
add code for a pytorch meet/join convolution layer

@@ -1,0 +1,85 @@
+import numpy as np
+import torch
+import torch.nn as nn 
+import torch.nn.functional as F
+import torch.optim as optim
+
+
+def build_meet_convolve_tensor(signal_dim,kernel_dim,kernel_loc):
+  # produces a tensor M_ijk such that the contraction M_ijk f_i is equal to f_{j ^ k}
+  M = torch.zeros(signal_dim,signal_dim,kernel_dim)
+  # this is an inefficient implementation, but should be fast enough for the sizes we're doing.
+  for i in range(signal_dim):
+    for j in range(i,signal_dim):
+      for k in range(kernel_dim):
+        if i == min(j,k+kernel_loc):
+          M[i,j,k] = 1
+  return M
+
+def build_join_convolve_tensor(signal_dim,kernel_dim,kernel_loc):
+  # produces a tensor M_ijk such that the contraction M_ijk f_i is equal to f_{j v k}
+  M = torch.zeros(signal_dim,signal_dim,kernel_dim)
+  for i in range(signal_dim):
+    for j in range(i,signal_dim):
+      for k in range(kernel_dim):
+        if i == max(j,k+kernel_loc):
+          M[i,j,k] = 1
+  return M
+
+class MeetConv2d(nn.Module):
+  def __init__(self,signal_dim,kernel_dim,kernel_loc,in_features,out_features):
+    super(MeetConv2d,self).__init__()
+    (signal_x, signal_y) = signal_dim
+    (kernel_x, kernel_y) = kernel_dim
+    (loc_x, loc_y) = kernel_loc
+    conv_x = build_meet_convolve_tensor(signal_x,kernel_x,loc_x)
+    conv_y = build_meet_convolve_tensor(signal_y,kernel_y,loc_y)
+    self.register_buffer('conv_x',conv_x)
+    self.register_buffer('conv_y',conv_y)
+    self.weights = nn.Parameter(torch.empty(kernel_x,kernel_y,in_features,out_features))
+    self.bias = nn.Parameter(torch.empty(signal_x,signal_y,out_features))
+    self.initialize_weights()
+
+  def initialize_weights(self):
+    nn.init.xavier_normal_(self.weights,gain=nn.init.calculate_gain('relu'))
+    nn.init.normal_(self.bias)
+    
+  def forward(self, X):
+    # X should be a (batchsize,signal_x,signal_y,in_features) tensor
[…]

### 2020-10-01 code/neural.py
fix size of bias parameter in convolution layers

@@ -37,7 +37,7 @@ class MeetConv2d(nn.Module):
     self.register_buffer('conv_x',conv_x)
     self.register_buffer('conv_y',conv_y)
     self.weights = nn.Parameter(torch.empty(kernel_x,kernel_y,in_features,out_features))
-    self.bias = nn.Parameter(torch.empty(signal_x,signal_y,out_features))
+    self.bias = nn.Parameter(torch.empty(out_features))
     self.initialize_weights()
 
   def initialize_weights(self):
@@ -48,7 +48,7 @@ class MeetConv2d(nn.Module):
     # X should be a (batchsize,signal_x,signal_y,in_features) tensor
     Y = torch.einsum("ixa,jyb,mijf,abzg->mxyg",self.conv_x,self.conv_y,X,self.weights)
     # Y is now (batchsize,signal_x,signal_y,out_features)
-    return Y + self.bias #this should broadcast over batchsize
+    return Y + self.bias #this should broadcast over everything
   
   def extra_repr(self):
     kernel_x, kernel_y, in_features, out_features = self.weights.shape
@@ -66,7 +66,7 @@ class JoinConv2d(nn.Module):
     self.register_buffer('conv_x',conv_x)
     self.register_buffer('conv_y',conv_y)
     self.weights = nn.Parameter(torch.empty(kernel_x,kernel_y,in_features,out_features))
-    self.bias = nn.Parameter(torch.empty(signal_x,signal_y,out_features))
+    self.bias = nn.Parameter(torch.empty(out_features))
     self.initialize_weights()
 
   def initialize_weights(self):
@@ -77,7 +77,7 @@ class JoinConv2d(nn.Module):
     # X should be a (batchsize,signal_x,signal_y,in_features) tensor
     Y = torch.einsum("ixa,jyb,mijf,abzg->mxyg",self.conv_x,self.conv_y,X,self.weights)
     # Y is now (batchsize,signal_x,signal_y,out_features)
-    return Y + self.bias #this should broadcast over batchsize
+    return Y + self.bias #this should broadcast over everything
   
   def extra_repr(self):
     kernel_x, kernel_y, in_features, out_features = self.weights.shape

### 2020-10-06 code/neural.py
fixed the original commit with colab code so that it runs as it should; still need to double check some things in neural.py

@@ -4,7 +4,6 @@ import torch.nn as nn
 import torch.nn.functional as F
 import torch.optim as optim
 
-
 def build_meet_convolve_tensor(signal_dim,kernel_dim,kernel_loc):
   # produces a tensor M_ijk such that the contraction M_ijk f_i is equal to f_{j ^ k}
   M = torch.zeros(signal_dim,signal_dim,kernel_dim)
@@ -19,6 +18,7 @@ def build_meet_convolve_tensor(signal_dim,kernel_dim,kernel_loc):
 def build_join_convolve_tensor(signal_dim,kernel_dim,kernel_loc):
   # produces a tensor M_ijk such that the contraction M_ijk f_i is equal to f_{j v k}
   M = torch.zeros(signal_dim,signal_dim,kernel_dim)
+  # this is an inefficient implementation, but should be fast enough for the sizes we're doing.
   for i in range(signal_dim):
     for j in range(i,signal_dim):
       for k in range(kernel_dim):
@@ -26,7 +26,10 @@ def build_join_convolve_tensor(signal_dim,kernel_dim,kernel_loc):
           M[i,j,k] = 1
   return M
 
-# building these arrays beforehand means we don't have to try to write complicated torch invocations to extract the right elements, which might not work very well on the GPU. This way convolution is "just" a tensor contraction.
+
+# to compute a convolution (f*g)_{xy}, we need to calculate the contraction M_{ixa} N_{jyb} f_{ij} g_{ab}
+def lattice_convolution_2d(convolve_x,convolve_y,signal,kernel):
+  return torch.einsum("ixa,jyb,ij,ab->xy",convolve_x,convolve_y,signal,kernel)
 
 class MeetConv2d(nn.Module):
   def __init__(self,signal_dim,kernel_dim,kernel_loc,in_features,out_features):
@@ -39,7 +42,7 @@ class MeetConv2d(nn.Module):
     self.register_buffer('conv_x',conv_x)
     self.register_buffer('conv_y',conv_y)
     self.weights = nn.Parameter(torch.empty(kernel_x,kernel_y,in_features,out_features))
-    self.bias = nn.Parameter(torch.empty(out_features))
+    self.bias = nn.Parameter(torch.empty(out_features,1,1))
     self.initialize_weights()
 
   def initialize_weights(self):
@@ -72,7 +75,7 @@ class JoinConv2d(nn.Module):
     self.register_buffer('conv_x',conv_x)
[…]

### 2020-10-06 code/rivet.py

@@ -1,4 +1,5 @@
 import os
+import torch
 
 def write_rivet_input(data_matrix,filtration_function,k,name):
     filtration_matrix = filtration_function(data_matrix,k)
@@ -18,3 +19,16 @@ def rivet_find_invariants(data_file_name,output_file_name, h_dim, x_bins,y_bins)
     cmd = "./rivet_console " + data_file_name + " --betti -H "+str(h_dim) + " -x "+str(x_bins)+" -y "+str(y_bins) + " > "+output_file_name
     os.system(cmd)
     return None
+
+def rivet_output_to_features(output_file_name):
+    return None
+
+output_file_name = "training_monitor_h0_0.txt"
+f = open(output_file_name,'r')
+lines = f.readlines()
+for i,line in enumerate(lines):
+    if line == "Dimensions > 0:":
+        break
+print(lines)
+for j in range(i,len(lines)):
+    print(lines[j])

### 2020-10-06 code/rivet_get_features.py

@@ -1,0 +1,47 @@
+import os
+from convert_point_cloud import off_to_pointcloud
+from features import density_filtration
+from rivet import write_rivet_input,rivet_find_invariants
+import numpy as np
+import numpy.random as rd
+
+main_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
+training_data = []
+testing_data = []
+max_size = 3000
+k=100
+x_bins = 40
+y_bins = 40
+max_dist = 100
+for category in os.listdir(main_path):
+    path_train = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"+category+'/train/'
+    for index,filename in enumerate(os.listdir(path_train)):
+        if filename == ".DS_Store":
+            continue
+        path = path_train + filename
+        print(filename)
+        point_cloud = off_to_pointcloud(path)
+        if point_cloud.shape[0]>max_size:
+            indices = rd.randint(0,point_cloud.shape[0],max_size)
+            point_cloud = point_cloud[indices,:]
+        name = "/home/ubuntu/code/rivet-input/training_" + str(category)+"_" + str(index)+".txt"
+        write_rivet_input(point_cloud,density_filtration,k,max_dist,name)
+        for deg in range(1):
+            output_name = '/home/ubuntu/code/invariants/training_'+str(category)+ "_h"+ str(deg)+"_"+str(index)+".txt"
+            rivet_find_invariants(name,output_name,deg,x_bins,y_bins)
+
+    path_test = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"+category+'/test/'
+    for index,filename in enumerate(os.listdir(path_test)):
+        if filename == ".DS_Store":
+            continue
+        path = path_test + filename
+        print(filename)
+        point_cloud = off_to_pointcloud(path)
+        if point_cloud.shape[0]>max_size:
+            indices = rd.randint(0,point_cloud.shape[0],max_size)
+            point_cloud = point_cloud[indices,:]
+        name = "/home/ubuntu/code/rivet-input/testing_" + str(category)+"_" + str(index)+".txt"
+        write_rivet_input(point_cloud,density_filtration,k,max_dist,name)
+        for deg in range(1):
+            output_name = '/home/ubuntu/code/invariants/testing_'+str(category)+ "_h"+ str(deg)+"_"+str(index)+".txt"
+            rivet_find_invariants(name,output_name,deg,x_bins,y_bins)

### 2020-10-06 code/rivet_get_features.py
wrote function to parse rivet outputs

@@ -1,9 +1,10 @@
 import os
 from convert_point_cloud import off_to_pointcloud
 from features import density_filtration
-from rivet import write_rivet_input,rivet_find_invariants
+from rivet import write_rivet_input,rivet_find_invariants,parse_rivet_output
 import numpy as np
 import numpy.random as rd
+import torch
 
 main_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
 training_data = []
@@ -45,3 +46,20 @@ for category in os.listdir(main_path):
         for deg in range(1):
             output_name = '/home/ubuntu/code/invariants/testing_'+str(category)+ "_h"+ str(deg)+"_"+str(index)+".txt"
             rivet_find_invariants(name,output_name,deg,x_bins,y_bins)
+#----------------------------------------------------------------------------------------------------------------------
+data_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
+label_dict = {}
+for index,category in enumerate(os.listdir(data_path)):
+    v = torch.zeros(len(os.listdir(data_path)))
+    v[index] = 1.0
+    label_dict[category] = v
+
+path = '/home/ubuntu/code/invariants/'
+N = len(os.listdir(path))
+X = torch.empty(N,4,x_bins,y_bins)
+Y = torch.empty(N,10)
+for index,file_name in enumerate(os.listdir('/home/ubuntu/code/invariants/')):
+    X[index,:,:,:] = parse_rivet_output(file_name,x_bins,y_bins)
+    v = label_dict[filename.split('_')[1]]
+    Y[index,:] = v
+

### 2020-10-06 code/training.py

@@ -1,13 +1,6 @@
 import numpy as np
 import torch
-from puschel import normalize_array,p_convolve,local_max_pool
-
-def sigmoid(x):
-    return 1/(1+np.e**(-x))
-
-def relu(x):
-    return np.maximum(np.zeros(x.shape),x)
-
-
+import torch.nn as nn
+import torch.functional as F
 
 

### 2020-10-08 code/neural.py
training completed with the binary classificaiton with LatticeCNN

@@ -113,6 +113,7 @@ class LatticeClassifier(nn.Module):
     self.fc1 = nn.Linear(8*signal_dim[0]*signal_dim[1],32)
     self.fc2 = nn.Linear(32,32)
     self.fc3 = nn.Linear(32,n_classes)
+    self.sm = nn.Softmax(dim=0)
 
   def forward(self,x):
     batch_size = x.shape[0]
@@ -120,7 +121,8 @@ class LatticeClassifier(nn.Module):
     x = F.relu(self.fc1(torch.reshape(x,(batch_size,-1))))
     x = F.relu(self.fc2(x))
     x = self.fc3(x)
-    return x
+    output = self.sm(x)
+    return output
 
 class ConvClassifier(nn.Module):
   def __init__(self,signal_dim,n_features,n_classes):
@@ -129,7 +131,7 @@ class ConvClassifier(nn.Module):
     self.fc1 = nn.Linear(8*signal_dim[0]*signal_dim[1],32)
     self.fc2 = nn.Linear(32,32)
     self.fc3 = nn.Linear(32,n_classes)
-
+    self.sm = nn.Softmax(dim=0)
   def forward(self,x):
     batch_size = x.shape[0]
     for c in self.convolutions:
@@ -137,4 +139,5 @@ class ConvClassifier(nn.Module):
     x = F.relu(self.fc1(torch.reshape(x,(batch_size,-1))))
     x = F.relu(self.fc2(x))
     x = self.fc3(x)
-    return x
+    output = self.sm(x)
+    return output

### 2020-10-08 code/rivet.py

@@ -20,15 +20,39 @@ def rivet_find_invariants(data_file_name,output_file_name, h_dim, x_bins,y_bins)
     os.system(cmd)
     return None
 
-def rivet_output_to_features(output_file_name):
-    return None
+def str2tuple(string):
+    return tuple([int(t) for t in string[1:-1].split(',')])
 
-output_file_name = "training_monitor_h0_0.txt"
-f = open(output_file_name,'r')
-lines = f.readlines()
-for i,line in enumerate(lines):
-    if line == "Dimensions > 0:":
-        break
-print(lines)
-for j in range(i,len(lines)):
-    print(lines[j])
+def parse_rivet_output(output_file_name, x_bins, y_bins):
+    f = open(output_file_name,'r')
+    lines = f.readlines()
+    X = torch.zeros(4,x_bins,y_bins)
+    d = 0
+    for line in lines:
+        if line.strip() == "x-grades":
+            continue
+        if line.strip() == "y-grades":
+            continue
+        if line.strip() == "Dimensions > 0:":
+            #print(line)
+            continue
+        if line.strip() == "xi_0:":
+            #print(line)
+            d+=1
+            continue
+        if line.strip() == "xi_1:":
+            #print(line)
+            d+=1
+            continue    
+        if line.strip() == "xi_2:":
+            #print(line)
+            d+=1
+            continue
+        if line.strip() == '':
+            continue
+            
+        if line.strip()[0] == '(' and line.strip()[-1] == ')':
+            (x,y,f_xy) = str2tuple(line.strip())
+            X[d,x,y] = float(f_xy)
+    return X
+

### 2020-10-08 code/training.py

@@ -1,6 +1,80 @@
 import numpy as np
+import os
 import torch
 import torch.nn as nn
 import torch.functional as F
+import torch.optim as optim
+from rivet import parse_rivet_output
+from neural import LatticeClassifier
+from numpy.random import permutation
+from torch.utils.data import DataLoader,random_split
 
+x_bins = 40
+y_bins = 40
+#data_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
+data_path = 'C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/data/ModelNet10/ModelNet10/'
 
+#binary classificaiton
+categories = ('sofa','monitor')
+n_features = 4
+n_classes = len(categories)
+feature_dim = (40,40)
+label_dict = {}
+for index,category in enumerate(categories):
+    v = torch.zeros(len(categories))
+    v[index] = 1.0
+    label_dict[category] = v
+#path = '/home/ubuntu/code/invariants/'
+path = 'C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/invariants_binary/'
+N = len(os.listdir(path))
+files = os.listdir(path)
+X = torch.zeros(N,n_features,x_bins,y_bins)
+Y = torch.zeros(N,n_classes)
+for index,file_name in enumerate(files):
+    X[index,:,:,:] = parse_rivet_output(path+file_name,x_bins,y_bins)
+    v = label_dict[file_name.split('_')[1]]
+    Y[index,:] = v
+print(X.shape)
+print(Y.shape)
+data = [[X[index,:,:,:],Y[index,:]] for index in range(X.shape[0])]
+training_data,testing_data = random_split(data,[len(data) - len(data)//10,len(data)//10])
+trainloader = DataLoader(training_data,batch_size=5,shuffle=True)
+testloader = DataLoader(testing_data,batch_size=5,shuffle=True)
+
+#binary classification sofa vs. monitor
+model = LatticeClassifier(feature_dim,n_features,n_classes)
+
+criterion = nn.BCELoss()
+#optimizer = optim.SGD(model.parameters(),lr=0.001,momentum=0.9)
+optimizer = optim.Adam(model.parameters(),lr=0.001)
+for epoch in range(2): 
+    for i, data in enumerate(trainloader):
+        inputs, labels = data
+        optimizer.zero_grad()
+        # forward + backward + optimize
+        outputs = model(inputs)
+        loss = criterion(outputs, labels)
+        loss.backward()
[…]

### 2020-10-08 code/training.py
got up to 70% accuracy on binary small dataset. network stored in binary_class_3.pth

@@ -8,6 +8,7 @@ from rivet import parse_rivet_output
 from neural import LatticeClassifier
 from numpy.random import permutation
 from torch.utils.data import DataLoader,random_split
+import time
 
 x_bins = 40
 y_bins = 40
@@ -15,28 +16,26 @@ y_bins = 40
 data_path = 'C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/data/ModelNet10/ModelNet10/'
 
 #binary classificaiton
-categories = ('sofa','monitor')
+categories = ['sofa','monitor']
 n_features = 4
 n_classes = len(categories)
 feature_dim = (40,40)
-label_dict = {}
-for index,category in enumerate(categories):
-    v = torch.zeros(len(categories))
-    v[index] = 1.0
-    label_dict[category] = v
+label_dict = {category:index for index,category in enumerate(categories) }
+reverse_label_dict = {index:category for index,category in enumerate(categories) }
 #path = '/home/ubuntu/code/invariants/'
 path = 'C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/invariants_binary/'
 N = len(os.listdir(path))
 files = os.listdir(path)
 X = torch.zeros(N,n_features,x_bins,y_bins)
-Y = torch.zeros(N,n_classes)
+Y = torch.zeros(N)
 for index,file_name in enumerate(files):
     X[index,:,:,:] = parse_rivet_output(path+file_name,x_bins,y_bins)
     v = label_dict[file_name.split('_')[1]]
-    Y[index,:] = v
+    Y[index] = v
+Y = Y.type(torch.LongTensor)
 print(X.shape)
 print(Y.shape)
-data = [[X[index,:,:,:],Y[index,:]] for index in range(X.shape[0])]
+data = [[X[index,:,:,:],Y[index]] for index in range(X.shape[0])]
 training_data,testing_data = random_split(data,[len(data) - len(data)//10,len(data)//10])
 trainloader = DataLoader(training_data,batch_size=5,shuffle=True)
 testloader = DataLoader(testing_data,batch_size=5,shuffle=True)
@@ -44,9 +43,10 @@ testloader = DataLoader(testing_data,batch_size=5,shuffle=True)
 #binary classification sofa vs. monitor
 model = LatticeClassifier(feature_dim,n_features,n_classes)
 
-criterion = nn.BCELoss()
-#optimizer = optim.SGD(model.parameters(),lr=0.001,momentum=0.9)
[…]

### 2020-10-08 code/neural.py
fix standard convolutional classifier

@@ -135,8 +135,8 @@ class LatticeClassifier(nn.Module):
 class ConvClassifier(nn.Module):
   def __init__(self,signal_dim,n_features,n_classes):
     super(ConvClassifier,self).__init__()
-    self.convolutions = [nn.Conv2d(n_features,16,(4,4),1,padding=3),nn.Conv2d(16,16,(4,4),1,padding=3),nn.Conv2d(16,8,(4,4),1,padding=3)]
-    self.fc1 = nn.Linear(8*signal_dim[0]*signal_dim[1],32)
+    self.convolutions = [nn.Conv2d(n_features,16,(4,4),1),nn.Conv2d(16,16,(4,4),1),nn.Conv2d(16,8,(4,4),1)]
+    self.fc1 = nn.Linear(8*(signal_dim[0]-9)*(signal_dim[1]-9),32)
     self.fc2 = nn.Linear(32,32)
     self.fc3 = nn.Linear(32,n_classes)
 

### 2020-10-08 code/testing.py
added module for testing and made changes discussed on call to training.py

@@ -1,10 +1,0 @@
-import numpy as np
-from features import density_filtration
-from rivet import rivet_find_invariants,write_rivet_input
-k=10
-a = np.random.rand(100,2)
-print(a)
-name = "test_point_cloud"
-output_name = "test_invariants"
-write_rivet_input(a,density_filtration,k,"test_point_cloud")
-rivet_find_invariants(name,output_name,1,10,10)

### 2020-10-08 code/training.py

@@ -10,6 +10,10 @@ from numpy.random import permutation
 from torch.utils.data import DataLoader,random_split
 import time
 
+device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
+cpu = torch.device("cpu")
+
+
 x_bins = 40
 y_bins = 40
 #data_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
@@ -33,49 +37,51 @@ for index,file_name in enumerate(files):
     v = label_dict[file_name.split('_')[1]]
     Y[index] = v
 Y = Y.type(torch.LongTensor)
-print(X.shape)
-print(Y.shape)
+
+print('data has shape: '+ str(X.shape))
+print('labels has shape: ' + str(Y.shape))
+
 data = [[X[index,:,:,:],Y[index]] for index in range(X.shape[0])]
 training_data,testing_data = random_split(data,[len(data) - len(data)//10,len(data)//10])
-trainloader = DataLoader(training_data,batch_size=5,shuffle=True)
-testloader = DataLoader(testing_data,batch_size=5,shuffle=True)
+trainloader = DataLoader(training_data,batch_size=16,shuffle=True)
+testloader = DataLoader(testing_data,batch_size=50,shuffle=True)
 
 #binary classification sofa vs. monitor
-model = LatticeClassifier(feature_dim,n_features,n_classes)
+for trial in range(10):
+    model = LatticeClassifier(feature_dim,n_features,n_classes)
+    model = model.to(device)
+    start_time = time.time()
+    criterion = nn.CrossEntropyLoss()
+    optimizer = optim.Adam(model.parameters(),lr=0.001)
+    for epoch in range(5): 
+        for i, data in enumerate(trainloader):
+            inputs, labels = data
+            inputs = inputs.to(device)
+            labels = labels.to(device)
+            optimizer.zero_grad()
+            # forward + backward + optimize
+            outputs = model(inputs)
+            loss = criterion(outputs, labels)
+            loss.backward()
+            optimizer.step()
+            # print statistics
+            a_loss = loss.item()
+            print('[%d, %d, %5d] loss: %.3f' %
+                    (trial + 1,epoch + 1, i + 1, a_loss))
+        model_file = './trial_'+str(trial) + '_epoch_'+str(epoch)+'.pth'
+        torch.save(model.state_dict(), model_file)
+    print('Finished Training')
+    print("Training took %s seconds" % (time.time() - start_time))
 
-start_time = time.time()
[…]

### 2020-10-08 paper/paper.tex
begin assembling paper

@@
 \usepackage{siunitx}        % SI units
-
+\usepackage{amsmath,amssymb}
 \urlstyle{same}
@@
 %HANS's CONVENIENCES
+\usepackage{mymacros}
 
-\title{Sheaves, GNNs, and Pooling}
+\title{Multidimensional Persistence Module Classification via Lattice-Theoretic Convolutions}
 
@@
   % examples of more authors
-  % \And
-  % Coauthor \\
-  % Affiliation \\
+  \And
+  Jakob Hansen \\
+  Department of Mathematics \\
+  Ohio State University \\
+  Columbus, OH 43210 \\
+  \texttt{hansen.612@osu.edu}
   % Address \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sheaves}
+\section{Introduction}
 
-\section{Graph Neural Networks}
+Persistent homology has the ability to discern both the global topology \cite{}
+and local geometry \cite{} of finite metric spaces (e.g. embedded weighted
+graphs, point clouds in $\R^d$) making it a befitting feature for the purposes of
+training a neural network. Single-dimensional homological persistence has drawn
+recent attention in deep learning \cite{}. This is, in part, due to a wide range
+of efficient software libraries [?,?,?] for computing barcodes (in the
+``west-coast'' lingo) of filtrations (e.g. Rips, alpha, {C}ech, sub-levelset).
+Barcodes provide a compact shape descriptor for metric space data \cite{} that
+is stable with respect to Gromov-Hausdorff distance \cite{}. In a seminal paper
+\cite{}, Carlsson and Zomorodian show there is no such compact description for
+multi-parameter persistence.
 
-\section{Pooling}
+\section{Backgound}
+Due to space constraints, we can offer only a brief overview of multiparameter
+persistent homology. For a primer on persistent homology,
+see~\cite{ghrist_barcodes_2008,carlsson_topology_2009}; for multiparameter
+persistent homology, see~\cite{}. An introduction to lattices may be found in~\cite{}.
 
-\begin{ack}
-I would like to thank...
-\end{ack}
+\subsection{Rips complexes and persistent homology}
+Let $(\mathcal M,d)$ be a finite metric space. The \introduce{Vietoris-Rips
+  complex} of $\mathcal M$ at scale $r$ is the abstract simplicial complex
+$\text{Rips}_r(\mathcal M)$ whose simplices are subsets of $\mathcal M$ of
+diameter at most $r$. There is a natural inclusion $\text{Rips}_r(\mathcal M)
+\to \text{Rips}_{r'}(\mathcal M)$ for $r \leq r'$.
 
-\
+Applying the simplicial homology functor (with coefficients in a field $k$)
+$H_i$ to $\text{Rips}_r(\mathcal M)$ produces a sequence of vector spaces
+$PH_i(r)$. The inclusions $\text{Rips}_r(\mathcal M) \to
+\text{Rips}_{r'}(\mathcal M)$ induce maps $PH_i(r) \to PH_i(r')$, producing the
+data of \introduce{persistence module}. This structure can be compactly
+described as a functor from $\R$, viewed as a category via its standard order
+structure, to the category $\Vect_k$ of vector spaces over $k$. The simplicity
+of the category $\R$ gives these persistence modules simple structure: they
+decompose as direct sums of interval modules $I_{[a,b)}$, which have
+$I_{[a,b)}(r) = k$ for $a \leq r < b$ and zero otherwise. The maps are
+the identity where possible and the zero map otherwise.
+% is this the right shape for the intervals?
+
+This representation theoretic fact gives a representation\footnote{Heh.} of
+$\R$-indexed persistence modules via \introduce{barcodes} or
+\introduce{persistence diagrams}. Each bar $I_{[a,b)}$ in the barcode represents
+a homology class which is \introduce{born} at $a$ and \introduce{dies} at $b$.
+
+\subsection{Multiparameter persistence}
+The Rips construction produces a filtration of simplicial complexes from a
+finite metric space; it is natural to consider the behavior of the homology
+functor over a pair of coherent filtrations. Consider
+a finite metric space $(\mathcal M, d)$ and a filtration
+function $\rho:\mathcal M \to \R$. This data specifies a bifiltration of
+simplicial complexes given by
+\[\mathbb{X}_{r,t} = \text{Rips}_r{x \in \mathcal M \mid \rho(x) \leq t}.\]
+There is a natural inclusion $\mathbb{X}_{r,t} \hookrightarrow
+\mathbb{X}_{r',t'}$ whenever $(r,t) \leq (r',t')$ in the lattice $\R \times R$.
+Composing with the homology functor produces a 2-parameter persistence module
+\[PH_{i}: \R_+ \times \R \to \Vect; \quad (r,t) \mapsto H_i(X_{r,t}).\]
+If we assume that (i) $PH_i$ stabilizes for $r \geq R$ and $t \geq T$ for
+sufficiently large $R, T$ and (ii) the induced map on homology
+$H_i(\mathbb{X}_{r,t}) \to H_i(\mathbb{X}_{r',t'})$ is an isomorphism for all
+but finitely many pairs $(r,t) \leq (r',t')$, then we can restrict the domain of
+our persistence module $PH_i$---possibly after a reparameterization of the
+filtration---to a finite order lattice $L = [m] \times [n]$, where $[n] =
+\{0,1,2,\ldots,n\}$, obtaining a persistence module $M: L \to \Vect$.
+% I'm not sure this is the right finiteness condition. It's very strong for an
+% $\R^2$-indexed peristence module.
+% we can also pull a persistence module back over an inclusion of a finite subset...
+More generally, this model accepts as inputs signals on any finite lattice $L$
+with features extracted from a generalized persistence module supported on $L$.
+
+%% something about why lattice convolutions make sense to use...
+
+From $M$, we extract two types of features:
+ the \introduce{Hilbert function}
+  \[\text{Hilb}: L \to \Z_+;\quad \mathbf{x} \mapsto \dim(M_\mathbf{x}),\] and
+the \introduce{multi-graded Betti numbers}\footnote{\textit{Caveat lector:} the
+multi-graded Betti numbers are not the same as the topological Betti numbers
+$\beta_i(\mathbb{X}) = \dim(H_i(\mathbb{X}))$.} $\xi_j: L \to \Z_+$, for $j =
+0,1,2$. For $M = PH_i$ as above, the Hilbert function counts the number of
+connected components ($i=0$), cycles ($i=1$), or higher dimensional voids ($i >
+1$) of the complex $\mathbb{X}_{r,t}$ at each $(r,t) \in L$. The multi-graded
+Betti numbers, on the other hand, capture information about locations of births
+and deaths of persistence classes.
+
+\subsection{Lattice-theoretic signal processing}
+
+\section{Lattice Convolutional Neural Networks}
+
+Convolutions for signals defined over $\R^n$ taken as an abelian group are
+widely used in signal processing. In particular, two-dimensional convolutions
+have served as an easily parameterized and efficient set of linear operations
+adapted to the structure of images. Their extreme utility in computer vision
+problems is owed to the translation equivariance properties of images: humans
+naturally recognize an image translated via an additive reparameterization as
+equivalent to the original.
+
+The data of a multidimensional persistence module is also indexed by $\R^n$ or a
+regular finite subset thereof, but its natural algebraic structure is not that
+of an abelian group. Rather, with its partial order structure, the indexing set
+is a lattice. In processing signals associated with the persistence module, it
+may be useful to take this structure into account rather than imposing the
+abelian group structure implied by standard convolutions.
+
+To this end, we construct a lattice convolution-based neural network layer
+suitable for use with features originating from multidimensional persistence
+modules.
+
+\section{Experiments}
+We use a small portion of the Princeton ModelNet dataset as a source of finite
+metric spaces. This dataset consists of hundreds of 3-dimensional CAD models
+representing objects from 40 classes. We select two of the classes and sample
+points from the 3d models to produce finite metric spaces embedded in $\R^3$.
+We then compute the corresponding multidimensional persistence modules, from
+which we produce features used as an input to a convolutional neural net
+classifier.
+
+As the filter function on these data sets, we use
+\[\rho_{\text{codense}}(x;k) = \frac{k \diam(\mathcal M)}{\sum_{y \in N_k(x)}
+    d(x,y)},\]
+where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$. This is the
+\introduce{codensity} filtration, so named because the points in the densest
+regions of $\mathcal M$ will appear first. A folk theorem is that the
+two-parameter persistent homology of a Rips/codensity bifiltration is stable
+under non-Hausdorff perturbations: \textit{the (Rips) persistent homology of a
+  point sample and another obtained by adding a small number of points at random
+are close with respect to the interleaving distance}.
+
+\section{Discussion}
+
+\bibliographystyle{alpha}
+\bibliography{sheafspectra}
 

### 2020-10-09 paper/paper.tex
add some citations and more content to the paper

@@
 % ready for submission
-% \usepackage{neurips_2020}
+%\usepackage{neurips_2020_tda}
 
@@
 training a neural network. Single-dimensional homological persistence has drawn
-recent attention in deep learning \cite{}. This is, in part, due to a wide range
-of efficient software libraries [?,?,?] for computing barcodes (in the
+recent attention in deep learning \cite{hofer_deep_2017,pun_persistent-homology-based_2018,bruel-gabrielsson_topology_2020}. This is, in part, due to a wide range
+of efficient software libraries \cite{otter_roadmap_2017,henselman_matroid_2017,bauer_ripser:_2019} for computing barcodes (in the
 ``west-coast'' lingo) of filtrations (e.g. Rips, alpha, {C}ech, sub-levelset).
-Barcodes provide a compact shape descriptor for metric space data \cite{} that
+Barcodes provide a compact shape descriptor for metric space data that
 is stable with respect to Gromov-Hausdorff distance \cite{}. In a seminal paper
-\cite{}, Carlsson and Zomorodian show there is no such compact description for
+\cite{carlsson_theory_2009}, Carlsson and Zomorodian show there is no such compact description for
 multi-parameter persistence.
@@
 persistent homology. For a primer on persistent homology,
-see~\cite{ghrist_barcodes_2008,carlsson_topology_2009}; for multiparameter
+see~\cite{ghrist_barcodes:_2008,carlsson_topology_2009}; for multiparameter
 persistent homology, see~\cite{}. An introduction to lattices may be found in~\cite{}.
@@
 
-From $M$, we extract two types of features:
+While there does not exist a discrete set of invariants for $M$, we can extract
+meaningful features. Two particularly informative types of features are 
  the \introduce{Hilbert function}
@@
 
-\subsection{Lattice-theoretic signal processing}
+\subsection{Lattice-theoretic signal processing}\label{sec:latticeconv}
 
-\section{Lattice Convolutional Neural Networks}
+\section{Lattice Convolutional Neural Networks}\label{sec:latticeCNN}
 
@@
 suitable for use with features originating from multidimensional persistence
-modules.
+modules. We specialize the convolutions described in
+Section~\ref{sec:latticeconv} to the particular case of regular finite
+sublattices of $\R^2$. The meet and join operations are easily computed
+elementwise:
+\[(r,t) \wedge (r',t') = (\min(r,r'),\min(t,t'));\quad (r,t)\vee (r',t') =
+  (\max(r,r'),\max(t,t')).\]
+
+A lattice convolution layer takes as input an $N_{\text{in}}$-dimensional signal
+$f : [m] \times [n] \to \R^{N_{\text{in}}}$ and outputs an
+$N_{\text{out}}$-dimensional signal $ [m] \times [n] \to
+\R^{N_{\text{out}}}$. The layer's parameters are given by a function $g: [m]
+\times [n] \to \R^{N_{\text{out}}\times N_{\text{in}}}$. If we label the
+entries of $f(x,y)$ by $f_i$ and the entries of $g(x,y)$ by $g^i_j$ The layer then acts by
+\[\text{MeetConv}(f)(x,y)^j = \sum_{i} (f_i \ast_{\wedge} g^i_j)(x,y) = \sum_i
+  \sum_{(a,b) \in [m]\times [n]} f_i(x \wedge a, y \wedge b)g^i_j(a,b)\]
+in the case of convolution with respect to the meet operation, and
+\[\text{JoinConv}(f)(x,y)^j = \sum_{i} (f_i \ast_{\vee} g^i_j)(x,y) = \sum_i
+  \sum_{(a,b) \in [m]\times [n]} f_i(x \vee a, y \vee b)g^i_j(a,b)\]
+in the case of convolution with respect to the join operation.
+
+Convolutional neural networks are uesful in part because the convolution kernels
+(here the functions $g$) can have very small support, enforcing locality and
+reducing the number of parameters that must be learned. In the standard
+convolutional setting, these kernels are implicitly supported in a neighborhood
+of the origin, but the location of the kernel is not usually explicitly
+specified. In the lattice setting, we do need to specify where the kernel
+resides. Just as when we treat our domain as an abelian group, the kernel should
+be supported near the identity, when we treat our domain as a lattice, the
+kernel should be supported near the neutral element of the operation. That is,
+for a meet convolution, $g$ should have support near the maximum $(m,n)$, and
+for a join convolution, $g$ should have support near the minimum $(0,0)$.
 
@@
 classifier.
+
+The pipline thus begins with a 3d model, which is sampled to produce a point
+cloud in $\R^3$. This point cloud then produces a bifiltered simplicial complex,
+whose persistent homology we calculate using RIVET~\cite{lesnick_interactive_2015}, producing
+lattice-indexed signals given by the Hilbert function and the multi-graded Betti
+numbers. These are then passed to the classifier, which produces a class prediction.
 
@@
 
+We compare the performance of two convolutional networks on this classification
+task. One uses the lattice-convolution based layers described in
+Section~\ref{sec:latticeCNN}, and the other uses standard convolutional layers.
+Each has three convolutional layers followed by three fully connected layers.
+
 \section{Discussion}
+Discuss.
 
-\bibliographystyle{alpha}
-\bibliography{sheafspectra}
+\bibliographystyle{plain}
+\bibliography{latticenn}
 

### 2020-10-09 code/main.py
additional changes to training.py with testing accuracy

@@ -1,46 +1,0 @@
-import os
-from convert_point_cloud import off_to_pointcloud
-from features import density_filtration
-from rivet import write_rivet_input,rivet_find_invariants
-import random
-
-main_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
-training_data = []
-testing_data = []
-for category in os.listdir(main_path):
-    path_train = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"+category+'/train/'
-    for index,filename in enumerate(os.listdir(path_train)):
-        if filename == ".DS_Store":
-            continue
-        path = path_train + filename
-        print(filename)
-        point_cloud = off_to_pointcloud(path)
-        training_data.append((point_cloud,category,index))
-    path_test = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"+category+'/test/'
-    for index,filename in enumerate(os.listdir(path_test)):
-        if filename == ".DS_Store":
-            continue
-        path = path_test + filename
-        print(filename)
-        point_cloud = off_to_pointcloud(path)
-        testing_data.append((point_cloud,category,index))
-
-random.shuffle(training_data)
-random.shuffle(testing_data)
-k=100
-x_bins = 10
-y_bins = 10
-
-for (point_cloud,label,index) in training_data:
-    name = "training_point_cloud_" + str(label)+"-" + str(index)+".txt"
-    write_rivet_input(point_cloud,density_filtration,k,name)
-    for deg in range(2):
-        output_name = 'training_invariants_deg_'+str(deg)+ "_"+ str(label)+"-"+str(index)+".txt"
-        rivet_find_invariants(name,output_name,deg,x_bins,y_bins)
-
-for (point_cloud,label,index) in testing_data:
-    name = "testing_point_cloud_" + str(label)+"-"+str(index)+".txt"
-    write_rivet_input(point_cloud,density_filtration,k,name)
-    for deg in range(2):
-        output_name = 'testing_invariants_deg_'+str(deg)+ "_"+ str(label)+"-"+str(index)+".txt"
-        rivet_find_invariants(name,output_name,deg,x_bins,y_bins)

### 2020-10-09 code/neural.py

@@ -98,8 +98,8 @@ class LatticeCNN(nn.Module):
     self.meet_conv = []
     self.join_conv = []
     for i in range(len(n_features)-1):
-      self.meet_conv.append(MeetConv2d(signal_dim,kernel_dim,(signal_dim[0]-kernel_dim[0],signal_dim[1]-kernel_dim[1]),n_features[i],n_features[i+1]))
-      self.join_conv.append(JoinConv2d(signal_dim,kernel_dim,(0,0),n_features[i],n_features[i+1]))
+      self.meet_conv.append(MeetConv2d(signal_dim,kernel_dim,(signal_dim[0]-kernel_dim[0],signal_dim[1]-kernel_dim[1]),n_features[i],n_features[i+1]).cuda())
+      self.join_conv.append(JoinConv2d(signal_dim,kernel_dim,(0,0),n_features[i],n_features[i+1]).cuda())
 
   def forward(self,x):
     for (mc,jc) in zip(self.meet_conv,self.join_conv):
@@ -110,10 +110,10 @@ class LatticeClassifier(nn.Module):
   def __init__(self,signal_dim,n_features,n_classes):
     super(LatticeClassifier,self).__init__()
     self.convolutions = LatticeCNN(signal_dim,(4,4),[n_features,16,16,8])
+    self.convolutions.cuda()
     self.fc1 = nn.Linear(8*signal_dim[0]*signal_dim[1],32)
     self.fc2 = nn.Linear(32,32)
     self.fc3 = nn.Linear(32,n_classes)
-    self.sm = nn.Softmax(dim=0)
 
   def forward(self,x):
     batch_size = x.shape[0]
@@ -121,8 +121,7 @@ class LatticeClassifier(nn.Module):
     x = F.relu(self.fc1(torch.reshape(x,(batch_size,-1))))
     x = F.relu(self.fc2(x))
     x = self.fc3(x)
-    output = self.sm(x)
-    return output
+    return x
 
 class ConvClassifier(nn.Module):
   def __init__(self,signal_dim,n_features,n_classes):
@@ -131,7 +130,6 @@ class ConvClassifier(nn.Module):
     self.fc1 = nn.Linear(8*(signal_dim[0]-9)*(signal_dim[1]-9),32)
     self.fc2 = nn.Linear(32,32)
     self.fc3 = nn.Linear(32,n_classes)
-    self.sm = nn.Softmax(dim=0)
   def forward(self,x):
[…]

### 2020-10-09 code/training.py

@@ -5,14 +5,15 @@ import torch.nn as nn
 import torch.functional as F
 import torch.optim as optim
 from rivet import parse_rivet_output
-from neural import LatticeClassifier
+from neural import LatticeClassifier,ConvClassifier
 from numpy.random import permutation
 from torch.utils.data import DataLoader,random_split
 import time
+from matplotlib.pyplot import figure,xlabel,ylabel,plot,savefig
+import pickle
 
 device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
 cpu = torch.device("cpu")
-
 
 x_bins = 40
 y_bins = 40
@@ -43,21 +44,23 @@ print('labels has shape: ' + str(Y.shape))
 
 data = [[X[index,:,:,:],Y[index]] for index in range(X.shape[0])]
 training_data,testing_data = random_split(data,[len(data) - len(data)//10,len(data)//10])
-trainloader = DataLoader(training_data,batch_size=16,shuffle=True)
-testloader = DataLoader(testing_data,batch_size=50,shuffle=True)
+trainloader = DataLoader(training_data,batch_size=16,shuffle=True,pin_memory=True)
+testloader = DataLoader(testing_data,batch_size=1,shuffle=True,pin_memory=True)
 
 #binary classification sofa vs. monitor
-for trial in range(10):
+n_trials = 5
+n_epochs = 15
+
+for trial in range(n_trials):
+    start_time = time.time()
     model = LatticeClassifier(feature_dim,n_features,n_classes)
     model = model.to(device)
-    start_time = time.time()
+    model.cuda()
     criterion = nn.CrossEntropyLoss()
     optimizer = optim.Adam(model.parameters(),lr=0.001)
-    for epoch in range(5): 
+    for epoch in range(n_epochs): 
         for i, data in enumerate(trainloader):
-            inputs, labels = data
-            inputs = inputs.to(device)
-            labels = labels.to(device)
+            inputs, labels = data[0].to(device), data[1].to(device)
             optimizer.zero_grad()
             # forward + backward + optimize
             outputs = model(inputs)
@@ -71,17 +74,34 @@ for trial in range(10):
         model_file = './trial_'+str(trial) + '_epoch_'+str(epoch)+'.pth'
         torch.save(model.state_dict(), model_file)
     print('Finished Training')
-    print("Training took %s seconds" % (time.time() - start_time))
+    print("Training took %.3f seconds" % (time.time() - start_time))
 
-# total = 0
-# correct = 0
[…]

### 2020-10-09 code/training.py
uptday to training.py

@@ -9,7 +9,7 @@ from neural import LatticeClassifier,ConvClassifier
 from numpy.random import permutation
 from torch.utils.data import DataLoader,random_split
 import time
-from matplotlib.pyplot import figure,xlabel,ylabel,plot,savefig
+from matplotlib.pyplot import figure,xlabel,ylabel,plot,savefig,legend,title
 import pickle
 
 device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
@@ -48,12 +48,63 @@ trainloader = DataLoader(training_data,batch_size=16,shuffle=True,pin_memory=Tru
 testloader = DataLoader(testing_data,batch_size=1,shuffle=True,pin_memory=True)
 
 #binary classification sofa vs. monitor
-n_trials = 5
-n_epochs = 15
-
+n_trials = 10
+n_epochs = 10
+#LatticeClassifier
 for trial in range(n_trials):
+    print('Next trial...')
     start_time = time.time()
     model = LatticeClassifier(feature_dim,n_features,n_classes)
+    model = model.to(device)
+    model.cuda()
+    criterion = nn.CrossEntropyLoss()
+    #optimizer = optim.Adam(model.parameters(),lr=0.001)
+    optimizer = optim.SGD(model.parameters(),lr=0.001)
+    for epoch in range(n_epochs): 
+        for i, data in enumerate(trainloader):
+            inputs, labels = data[0].to(device), data[1].to(device)
+            optimizer.zero_grad()
+            # forward + backward + optimize
+            outputs = model(inputs)
+            loss = criterion(outputs, labels)
+            loss.backward()
+            optimizer.step()
+            # print statistics
+            a_loss = loss.item()
+            print('[%d, %d, %5d] loss: %.3f' %
+                    (trial + 1,epoch + 1, i + 1, a_loss))
+        model_file = './training/trial_'+str(trial) + '_epoch_'+str(epoch)+'.pth'
+        torch.save(model.state_dict(), model_file)
+    print('Finished Training LatticeClassifier.')
+    print("Training took %.d seconds" % (time.time() - start_time))
+print('Testing accuracy of LatticeClassifier...')
+accuracy = torch.zeros(n_epochs,n_trials)
+with torch.no_grad():
+    for trial in range(n_trials):
+        for epoch in range(n_epochs):
+            total = 0
+            correct = 0
[…]

### 2020-10-09 paper/paper.tex
update to training.py; worked on paper introduction

@@
 
-Persistent homology has the ability to discern both the global topology \cite{}
+Persistent homology has the ability to discern both the global topology \cite{ghrist_barcodes:_2008}
 and local geometry \cite{} of finite metric spaces (e.g. embedded weighted
@@
 Barcodes provide a compact shape descriptor for metric space data that
-is stable with respect to Gromov-Hausdorff distance \cite{}. In a seminal paper
-\cite{carlsson_theory_2009}, Carlsson and Zomorodian show there is no such compact description for
-multi-parameter persistence.
+is stable with respect to Gromov-Hausdorff distance \cite{}.
+What's more, barcodes are encodable as features for performing various machine learning tasks (e.g.~classification).
+Competing recipes for featurizing barcodes from single dimensional persistence, including persistence images \cite{}, persistence landscapes \cite{}, and more exotic methods \cite{tropical}, are gaining momentum in machine learning and other scientific spheres.
+
+Multidimensional persistence generalizes single-dimensional persistent homology in order to tackle filtrations parameterized in multiple dimensions.
+Such filtrations arise, for example, in a Rips filtration of a finite metric space (i.e.~a Rips filtration) for which the finite metric space itself is parameterized by a signal attributing a vector in $\R^d$ to every point of the metric space.
+Restricting to points in the metric space appearing below a certain coordinate-wise threshold results in a mulit-filtration of the cooresponding Rips complexes.
+
+Multidimensional persistence boasts stability properties \cite{lesnick_theory_2015}, if computational intractable.
+While these properties are impressive, they avert a combinatorial description akin to the barcode.
+This is not by accident.
+In fact, no such compact description for
+multidimensional persistence is possible \cite{carlsson_theory_2009}.
+All hope is not lost. Families of integer-valued maps over the parameter space of a persistence module called \textit{invariants} have qualified ability to characterize multidimensional persistence.
+Invariants considered in this paper are include the \textit{Hilbert function}, indicating the rank of homology at a particular point in parameter space, and the \textit{multi-graded Betti numbers}, a family of discrete algebraic invariants arising from a construction in homological algebra; the Hilbert function is nothing more than parametrized (topological) Betti numbers\footnote{\textit{Caveat lector:} the
+multi-graded Betti numbers are not the same as the topological Betti numbers
+$\beta_i(\mathbb{X}) = \dim(H_i(\mathbb{X}))$.}, the muilti-graded Betti numbers have their own geometric interpretation \cite{Knudson2008}.
+The \textit{rank invariant}, another invariant, is shown to be complete in the case of single dimensional persistence \cite{carlsson_theory_2009}; due to it's difficulty to compute it is not considered here.
+
+Multidimensional persistence suffers several hindrances to its usefulness in machine learning.
+(i) Software for computing invariants for multidimensional persistence is scarce.
+To the authors' knowledge, RIVET is the only available software for computing multidimensional persistence \cite{lesnick_interactive_2015}; RIVET specializes to $2$-dimensional persistence and provides a user-interface for visualizing multi-filtrations as well as a pipline for computing the Hilbert function and the multi-graded Betti numbers in degrees $0$, $1$, and $2$.
+(ii) For all the attention multidimensional persistence has received, there has been no activity, as far as the authors are aware, studying generating features from multidimensional persistence modules.
+
+We hope to ignite an interest in filling both of these gaps.
+In this paper, we propose a naive featurization of multidimensional persistence modules based on the invariants aforementioned.
+We design an architecture for classifying these persistence modules.
+Our architecture employs a lattice-theoretic notion of convolution, thereby respecting the order relation of the parameters of the persistence module.
+We implement our model and compare the performance of our proposed lattice-convolutional architecture with a (simplified) standard convolutional architecture (e.g.~similar to ImageNET).
 
@@
 
-This representation theoretic fact gives a representation\footnote{Heh.} of
+This representation theoretic fact gives a representation\footnote{Pun intended.} of
 $\R$-indexed persistence modules via \introduce{barcodes} or
@@
   \[\text{Hilb}: L \to \Z_+;\quad \mathbf{x} \mapsto \dim(M_\mathbf{x}),\] and
-the \introduce{multi-graded Betti numbers}\footnote{\textit{Caveat lector:} the
-multi-graded Betti numbers are not the same as the topological Betti numbers
-$\beta_i(\mathbb{X}) = \dim(H_i(\mathbb{X}))$.} $\xi_j: L \to \Z_+$, for $j =
+the \introduce{multi-graded Betti numbers} $\xi_j: L \to \Z_+$, for $j =
 0,1,2$. For $M = PH_i$ as above, the Hilbert function counts the number of

### 2020-10-09 paper/paper.tex
minor
add section on lattice signal processing, cut other material ruthlessly

--- 2020-10-09 paper/paper.tex
@@
 \begin{abstract}
- To write...
+ We consider the use of lattice-based convolutional neural network layers as a 
+ tool for the analysis of features arising from multiparameter persistence
+ modules. \textbf{CHANGE THIS: something something the conclusion about what to do}
 \end{abstract}
@@
 
-Persistent homology has the ability to discern both the global topology \cite{}
-and local geometry \cite{} of finite metric spaces (e.g. embedded weighted
-graphs, point clouds in $\R^d$) making it a befitting feature for the purposes of
-training a neural network. Single-dimensional homological persistence has drawn
-recent attention in deep learning \cite{hofer_deep_2017,pun_persistent-homology-based_2018,bruel-gabrielsson_topology_2020}. This is, in part, due to a wide range
-of efficient software libraries \cite{otter_roadmap_2017,henselman_matroid_2017,bauer_ripser:_2019} for computing barcodes (in the
-``west-coast'' lingo) of filtrations (e.g. Rips, alpha, {C}ech, sub-levelset).
-Barcodes provide a compact shape descriptor for metric space data that
-is stable with respect to Gromov-Hausdorff distance \cite{}. In a seminal paper
-\cite{carlsson_theory_2009}, Carlsson and Zomorodian show there is no such compact description for
-multi-parameter persistence.
+Persistent homology has the ability to discern both the global
+topology~\cite{ghrist_barcodes:_2008} and local
+geometry~\cite{bubenik_persistent_2020} of finite metric spaces (e.g. embedded
+weighted graphs, point clouds in $\R^d$) making it a befitting feature for the
+purposes of training a neural network. Single-dimensional homological
+persistence has drawn recent attention in deep learning~\cite{hofer_deep_2017,
+pun_persistent-homology-based_2018, bruel-gabrielsson_topology_2020}. This is,
+in part, due to a wide range of efficient software
+libraries~\cite{otter_roadmap_2017, henselman_matroid_2017, bauer_ripser:_2019}
+for computing persistent homology, %barcodes (in the ``west-coast'' lingo) of
+% filtrations,
+as well as a growing cookbook of recipes 
+for featurizing barcodes from single dimensional persistence, including
+persistence images~\cite{adams_persistence_2017}, persistence
+landscapes~\cite{bubenik_statistical_2015}, and more exotic methods
+\cite{kalisnik_tropical_2019}.
+
+Multidimensional persistence generalizes single-dimensional persistent homology
+in order to tackle filtrations parameterized in multiple dimensions.
+% Such
+% filtrations arise, for example, in a Rips filtration of a finite metric space
+% for which the finite metric space itself carries a filter function. %is parameterized by a signal
+% %attributing a vector in $\R^d$ to every point of the metric space.
+% Restricting
+% to points in the metric space appearing below a certain coordinate-wise
+% threshold results in a multi-filtration of the corresponding Rips complexes.
+%Multidimensional persistence boasts stability properties similar to those in one
+%dimension~\cite{lesnick_theory_2015}.
+Unfortunately, there is no complete
+compact barcode-like characterization of multidimensional persistence
+modules~\cite{carlsson_theory_2009}. We must make do with incomplete invariants.
+There are various algebraic invariants; in this paper we will use the
+\textit{Hilbert function} and the \textit{multi-graded Betti numbers}, both of
+which are $\mathbb{N}$-valued functions on the parameter space.
+%Their names arise from their relationship with the homological algebra of
+%persistence modules.
+The Hilbert function is nothing more than the pointwise
+(topological) Betti numbers\footnote{\textit{Caveat lector:} the multi-graded
+Betti numbers are not the same as the topological Betti numbers
+$\beta_i(\mathbb{X}) = \dim(H_i(\mathbb{X}))$.}, and the multi-graded Betti
+numbers have an interpretation in terms of births and deaths~\cite{knudson_refinement_2008}.
+
+% The \textit{rank
+% invariant}, another invariant, is shown to be complete in the case of single
+% dimensional persistence \cite{carlsson_theory_2009}; due to its difficulty to
+% compute it is not considered here.
+
+Multidimensional persistence suffers two hindrances to its usefulness in
+machine learning. First, software for computing multidimensional persistence is
+scarce. To the authors' knowledge, RIVET is the only available software for
+computing multidimensional persistence~\cite{lesnick_interactive_2015}; RIVET
+specializes to $2$-dimensional persistence and is focused on interactive
+visualization rather than machine-interpretable output.
+% provides a user-interface for
+% visualizing multi-filtrations as well as a pipline for computing the Hilbert
+% function and the multi-graded Betti numbers in degrees $0$, $1$, and $2$.
+Second, %for all the attention multidimensional persistence has received,
+there has been no activity, as far as the authors are aware, studying the extraction
+of suitable features for multidimensional persistent homology.
+
+We hope to ignite an interest in filling both of these gaps. In this paper, we
+propose a naive featurization of multidimensional persistence modules based on
+the aforementioned invariants, and design an architecture for classifying these
+persistence modules. This architecture employs a lattice-theoretic notion of
+convolution, thereby respecting the order relation of the parameters of the
+persistence module. We implement our model and compare the performance of our
+proposed lattice-convolutional architecture with a (simplified) standard
+convolutional architecture.
 
 \section{Backgound}
+
 Due to space constraints, we can offer only a brief overview of multiparameter
 persistent homology. For a primer on persistent homology,
-see~\cite{ghrist_barcodes:_2008,carlsson_topology_2009}; for multiparameter
-persistent homology, see~\cite{}. An introduction to lattices may be found in~\cite{}.
+see~\cite{ghrist_barcodes:_2008, carlsson_topology_2009}; for multiparameter
+persistent homology, see~\cite{}. An introduction to lattices may be found
+in~\cite{}.
 
@@
 decompose as direct sums of interval modules $I_{[a,b)}$, which have
-$I_{[a,b)}(r) = k$ for $a \leq r < b$ and zero otherwise. The maps are
-the identity where possible and the zero map otherwise.
+$I_{[a,b)}(r) = k$ for $a \leq r < b$ and zero otherwise. The maps are the
+identity where possible and the zero map otherwise.
 % is this the right shape for the intervals?
 
-This representation theoretic fact gives a representation\footnote{Heh.} of
+This representation theoretic fact gives a representation\footnote{Pun intended.} of
 $\R$-indexed persistence modules via \introduce{barcodes} or
@@
 \[PH_{i}: \R_+ \times \R \to \Vect; \quad (r,t) \mapsto H_i(X_{r,t}).\]
-If we assume that (i) $PH_i$ stabilizes for $r \geq R$ and $t \geq T$ for
-sufficiently large $R, T$ and (ii) the induced map on homology
-$H_i(\mathbb{X}_{r,t}) \to H_i(\mathbb{X}_{r',t'})$ is an isomorphism for all
-but finitely many pairs $(r,t) \leq (r',t')$, then we can restrict the domain of
-our persistence module $PH_i$---possibly after a reparameterization of the
-filtration---to a finite order lattice $L = [m] \times [n]$, where $[n] =
-\{0,1,2,\ldots,n\}$, obtaining a persistence module $M: L \to \Vect$.
-% I'm not sure this is the right finiteness condition. It's very strong for an
-% $\R^2$-indexed peristence module.
-% we can also pull a persistence module back over an inclusion of a finite subset...
-More generally, this model accepts as inputs signals on any finite lattice $L$
-with features extracted from a generalized persistence module supported on $L$.
 
-%% something about why lattice convolutions make sense to use...
+% When the filtration of $\mathbb{X}$ is sufficiently nice, the persistence module
+% may be characterized on a finite domain...
+% If we assume that (i) $PH_i$ stabilizes for $r \geq R$ and $t \geq T$ for
+% sufficiently large $R, T$ and (ii) the induced map on homology
+% $H_i(\mathbb{X}_{r,t}) \to H_i(\mathbb{X}_{r',t'})$ is an isomorphism for all
+% but finitely many pairs $(r,t) \leq (r',t')$, then we can restrict the domain of
+% our persistence module $PH_i$---possibly after a reparameterization of the
+% filtration---to a finite order lattice $L = [m] \times [n]$, where $[n] =
+% \{0,1,2,\ldots,n\}$, obtaining a persistence module $M: L \to \Vect$.
+% % I'm not sure this is the right finiteness condition. It's very strong for an
+% % $\R^2$-indexed peristence module.
+% % we can also pull a persistence module back over an inclusion of a finite subset...
+% %More generally, this model accepts as inputs signals on any finite lattice $L$
+% %with features extracted from a generalized persistence module supported on $L$.
 
@@
  the \introduce{Hilbert function}
-  \[\text{Hilb}: L \to \Z_+;\quad \mathbf{x} \mapsto \dim(M_\mathbf{x}),\] and
-the \introduce{multi-graded Betti numbers}\footnote{\textit{Caveat lector:} the
-multi-graded Betti numbers are not the same as the topological Betti numbers
-$\beta_i(\mathbb{X}) = \dim(H_i(\mathbb{X}))$.} $\xi_j: L \to \Z_+$, for $j =
+  \[\text{Hilb}: R_+ \times R \to \Z_+;\quad \mathbf{x} \mapsto \dim(M_\mathbf{x}),\] and
+the \introduce{multi-graded Betti numbers} $\xi_j: L \to \Z_+$, for $j =
 0,1,2$. For $M = PH_i$ as above, the Hilbert function counts the number of
 connected components ($i=0$), cycles ($i=1$), or higher dimensional voids ($i >
-1$) of the complex $\mathbb{X}_{r,t}$ at each $(r,t) \in L$. The multi-graded
+1$) of the complex $\mathbb{X}_{r,t}$ at each $(r,t) \in R_+\times \R$. The multi-graded
 Betti numbers, on the other hand, capture information about locations of births
@@
 
+Classical signal processing proceeds by constructing filters for space- or
+time-indexed signals using convolutional operators. These implicitly rely on the
+algebraic properties of the underlying space, in particular the existence of
+well-behaved translation operators. This fact is exploited in the general
+framework of algebraic signal processing~\cite{puschel_algebraic_2008} and
+extended to more general domains by the theory of graph signal
+processing~\cite{ortega_graph_2018}. We here describe a similar extension to
+signals on a finite lattice proposed in~\cite{pueschel_discrete_2019}.
+
+A \introduce{lattice} $L$ is a partially ordered set in which every pair of
+elements $x,y$ has a greatest lower bound (the \introduce{meet} $x \wedge y$)
+and a least upper bound (the \introduce{join} $x \vee y$). These operations
+and their properties produce an algebraic characterization of lattices; the
+order theoretic and algebraic properties of a lattice can be recovered from each
+other. The key insight of~\cite{pueschel_discrete_2019} is that the meet and
+join operations on a lattice define two ``shift operators'' that can be
+exploited to define convolutional filters for signals on a lattice.
+
+That is, for two signals $f,g: L \to \R$, where $L$ is a lattice, we define
+\[(f *_\wedge g)(x) = \sum_{a \in L}f(x\wedge a)g(a) \;\;\text{and}\;\; (f *_\vee g)(x) = \sum_{a \in L}f(x\vee a)g(a).\]
+
+A particularly nice class of examples of lattices are given by the sets $\R^n$
+viewed as partially ordered sets, with the ordering $(x_1,\ldots,x_n) \leq
+(y_1,\ldots,y_n)$ whenever $x_i \leq y_i$ for all $1 \leq i \leq n$. These are,
+of course, the indexing sets for persistent homology, suggesting that lattice
+convolutions over $\R^n$ or its finite sublattices may be useful in analyzing
+data coming from multiparameter persistence computations.
+
 \section{Lattice Convolutional Neural Networks}\label{sec:latticeCNN}
 
-Convolutions for signals defined over $\R^n$ taken as an abelian group are
-widely used in signal processing. In particular, two-dimensional convolutions
+Convolutions over $\R^2$ (with its abelian group structure)
 have served as an easily parameterized and efficient set of linear operations
@@
 suitable for use with features originating from multidimensional persistence
-modules. We specialize the convolutions described in
+modules. To the authors' knowledge, such an architecture has not previously been
+described, although a special case (where the underlying lattice is a power set)
+has been implemented in~\cite{wendler_powerset_2019}. We specialize the convolutions described in
 Section~\ref{sec:latticeconv} to the particular case of regular finite
-sublattices of $\R^2$. The meet and join operations are easily computed
+sublattices of $\R^2$. These may be represented (up to isomorphism)as $L = [m]
+\times [n]$, where $[n]$ is the ordered set $\{0,1,\dots,n\}$. The meet and join operations are easily computed
 elementwise:
@@
 Convolutional neural networks are uesful in part because the convolution kernels
-(here the functions $g$) can have very small support, enforcing locality and
-reducing the number of parameters that must be learned. In the standard
-convolutional setting, these kernels are implicitly supported in a neighborhood
-of the origin, but the location of the kernel is not usually explicitly
-specified. In the lattice setting, we do need to specify where the kernel
-resides. Just as when we treat our domain as an abelian group, the kernel should
-be supported near the identity, when we treat our domain as a lattice, the
-kernel should be supported near the neutral element of the operation. That is,
-for a meet convolution, $g$ should have support near the maximum $(m,n)$, and
-for a join convolution, $g$ should have support near the minimum $(0,0)$.
+(here the functions $g$) can have very small support, reducing the number of
+parameters that must be learned. In the standard convolutional setting, these
+kernels are implicitly supported in a neighborhood of the origin, but the
+location of the kernel is not usually explicitly specified. In the lattice
+setting, we do need to specify where the kernel resides. In the abelian group
+case, the kernel is supported near the identity, and similarly, 
+when we treat our domain as a lattice, the kernel should be supported
+near the neutral element of the operation. That is, for a meet convolution, $g$
+should have support near the maximum $(m,n)$, and for a join convolution, $g$
+should have support near the minimum $(0,0)$.
 
 \section{Experiments}
-We use a small portion of the Princeton ModelNet dataset as a source of finite
+We use a small portion of the Princeton ModelNet
+dataset~\cite{zhirong_wu_3d_2015} as a source of finite
 metric spaces. This dataset consists of hundreds of 3-dimensional CAD models
 representing objects from 40 classes. We select two of the classes and sample
-points from the 3d models to produce finite metric spaces embedded in $\R^3$.
+points from the 3D models to produce finite metric spaces embedded in $\R^3$.
 We then compute the corresponding multidimensional persistence modules, from
@@
 
-The pipline thus begins with a 3d model, which is sampled to produce a point
+The pipline thus begins with a 3D model, which is sampled to produce a point
 cloud in $\R^3$. This point cloud then produces a bifiltered simplicial complex,
-whose persistent homology we calculate using RIVET~\cite{lesnick_interactive_2015}, producing
-lattice-indexed signals given by the Hilbert function and the multi-graded Betti
-numbers. These are then passed to the classifier, which produces a class prediction.
+whose persistent homology we calculate using
+RIVET~\cite{lesnick_interactive_2015}, sampled at a discrete grid of $40 \times
+40$ points, producing lattice-indexed signals given by the Hilbert function and
+the multi-graded Betti numbers. These are then passed to the classifier, which
+produces a class prediction.
 
@@
 \introduce{codensity} filtration, so named because the points in the densest
-regions of $\mathcal M$ will appear first. A folk theorem is that the
-two-parameter persistent homology of a Rips/codensity bifiltration is stable
-under non-Hausdorff perturbations: \textit{the (Rips) persistent homology of a
-  point sample and another obtained by adding a small number of points at random
-are close with respect to the interleaving distance}.
+regions of $\mathcal M$ will appear first.
+
+% A folk theorem is that the
+% two-parameter persistent homology of a Rips/codensity bifiltration is stable
+% under non-Hausdorff perturbations: \textit{the (Rips) persistent homology of a
+%   point sample and another obtained by adding a small number of points at random
+% are close with respect to the interleaving distance}.
 

### 2020-10-10 code/training.py
ran conv_accuracy succesfully

@@ -48,19 +48,23 @@ trainloader = DataLoader(training_data,batch_size=16,shuffle=True,pin_memory=Tru
 testloader = DataLoader(testing_data,batch_size=1,shuffle=True,pin_memory=True)
 
 #binary classification sofa vs. monitor
-n_trials = 10
-n_epochs = 10
+n_trials = 5
+n_epochs = 50
+train_accuracy = torch.zeros(n_epochs,n_trials)
+test_accuracy = torch.zeros(n_epochs,n_trials)
 #LatticeClassifier
 for trial in range(n_trials):
-    print('Next trial...')
+    print('New trial...')
     start_time = time.time()
     model = LatticeClassifier(feature_dim,n_features,n_classes)
     model = model.to(device)
     model.cuda()
     criterion = nn.CrossEntropyLoss()
-    #optimizer = optim.Adam(model.parameters(),lr=0.001)
-    optimizer = optim.SGD(model.parameters(),lr=0.001)
+    optimizer = optim.Adam(model.parameters(),lr=0.0001)
     for epoch in range(n_epochs): 
+        print('Epoch: '+str(epoch+1))
+        total = 0.0
+        correct = 0
         for i, data in enumerate(trainloader):
             inputs, labels = data[0].to(device), data[1].to(device)
             optimizer.zero_grad()
@@ -70,102 +74,132 @@ for trial in range(n_trials):
             loss.backward()
             optimizer.step()
             # print statistics
-            a_loss = loss.item()
-            print('[%d, %d, %5d] loss: %.3f' %
-                    (trial + 1,epoch + 1, i + 1, a_loss))
-        model_file = './training/trial_'+str(trial) + '_epoch_'+str(epoch)+'.pth'
-        torch.save(model.state_dict(), model_file)
-    print('Finished Training LatticeClassifier.')
-    print("Training took %.d seconds" % (time.time() - start_time))
-print('Testing accuracy of LatticeClassifier...')
-accuracy = torch.zeros(n_epochs,n_trials)
-with torch.no_grad():
-    for trial in range(n_trials):
-        for epoch in range(n_epochs):
-            total = 0
-            correct = 0
-            model = LatticeClassifier(feature_dim,n_features,n_classes)
-            model = model.to(device)
-            model_file = './training/trial_'+str(trial) + '_epoch_'+str(epoch)+'.pth'
-            model.load_state_dict(torch.load(model_file))
+            # a_loss = loss.item()
+            # print('[%d, %d, %5d] loss: %.3f' %
[…]

### 2020-10-10 code/training_conv.py

@@ -1,0 +1,114 @@
+import numpy as np
+import os
+import torch
+import torch.nn as nn
+import torch.functional as F
+import torch.optim as optim
+from rivet import parse_rivet_output
+from neural import LatticeClassifier,ConvClassifier
+from numpy.random import permutation
+from torch.utils.data import DataLoader,random_split
+import time
+from matplotlib.pyplot import figure,xlabel,ylabel,plot,savefig,legend,title
+import pickle
+
+device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
+cpu = torch.device("cpu")
+
+x_bins = 40
+y_bins = 40
+#data_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
+data_path = 'C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/data/ModelNet10/ModelNet10/'
+
+#binary classificaiton
+categories = ['sofa','monitor']
+n_features = 4
+n_classes = len(categories)
+feature_dim = (40,40)
+label_dict = {category:index for index,category in enumerate(categories) }
+reverse_label_dict = {index:category for index,category in enumerate(categories) }
+#path = '/home/ubuntu/code/invariants/'
+path = 'C:/Users/hansr/OneDrive/Documents/Research/NeurIPS20/code/invariants_binary/'
+N = len(os.listdir(path))
+files = os.listdir(path)
+X = torch.zeros(N,n_features,x_bins,y_bins)
+Y = torch.zeros(N)
+for index,file_name in enumerate(files):
+    X[index,:,:,:] = parse_rivet_output(path+file_name,x_bins,y_bins)
+    v = label_dict[file_name.split('_')[1]]
+    Y[index] = v
+Y = Y.type(torch.LongTensor)
+
+print('data has shape: '+ str(X.shape))
+print('labels has shape: ' + str(Y.shape))
+
+data = [[X[index,:,:,:],Y[index]] for index in range(X.shape[0])]
+training_data,testing_data = random_split(data,[len(data) - len(data)//10,len(data)//10])
+trainloader = DataLoader(training_data,batch_size=16,shuffle=True,pin_memory=True)
+testloader = DataLoader(testing_data,batch_size=1,shuffle=True,pin_memory=True)
+
+#binary classification sofa vs. monitor
+n_trials = 5
+n_epochs = 50
+train_accuracy = torch.zeros(n_epochs,n_trials)
[…]

### 2020-10-10 paper/paper.tex
add discussion

@@
   Department of Electrical and Systems Engineering \\
-  Universiyt of Pennsylvania\\
+  University of Pennsylvania\\
   Philadelphia, PA 19104 \\
@@
 \begin{abstract}
+ Multiparameter persistent homology has been largely neglected as an input to
+ machine learning algorithms.
  We consider the use of lattice-based convolutional neural network layers as a 
  tool for the analysis of features arising from multiparameter persistence
- modules. \textbf{CHANGE THIS: something something the conclusion about what to do}
+ modules. We find that these show promise as an alternative to convolutions for
+ the classification of multidimensional persistence modules.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 of suitable features for multidimensional persistent homology.
+%Carlsson has a little bit in a recent paper...
 
@@
 see~\cite{ghrist_barcodes:_2008, carlsson_topology_2009}; for multiparameter
-persistent homology, see~\cite{}. An introduction to lattices may be found
-in~\cite{}.
+persistent homology, see~\cite{lesnick_interactive_2015}. An introduction to
+lattices may be found in~\cite{}.
 
@@
 Section~\ref{sec:latticeconv} to the particular case of regular finite
-sublattices of $\R^2$. These may be represented (up to isomorphism)as $L = [m]
+sublattices of $\R^2$. These may be represented (up to isomorphism) as $L = [m]
 \times [n]$, where $[n]$ is the ordered set $\{0,1,\dots,n\}$. The meet and join operations are easily computed
@@
 \section{Experiments}
+\begin{figure}
+  \caption{Comparison training curves for the lattice neural network and
+    standard convolutional neural network.}\label{fig:comparison}
+\end{figure}
+
 We use a small portion of the Princeton ModelNet
@@
 the multi-graded Betti numbers. These are then passed to the classifier, which
-produces a class prediction.
+produces a class prediction, in this case either ``sofa'' or ``monitor.''
 
@@
 Each has three convolutional layers followed by three fully connected layers.
+The lattice-based convolution layers are of the form $\text{MeetConv}(x) +
+\text{JoinConv}(x)$. All convolution kernels have dimension $4 \times 4$, hidden
+convolution layers have 16 features, and the final convolution has 8 features.
+The fully connected layers have 32 features at each inner layer.
+The networks are trained using the Adam gradient algorithm with learning rate
+$0.001$ for 50 epochs. We reserve 10\% of the data for testing. Results are
+shown in Figure~\ref{fig:comparison}.
+
+The lattice-based convolution and classical convolution networks perform
+similarly on the training set. However, the lattice convolution network's
+predictions generalize more accurately to the testing set.
+%% more discussion of what the data actually looks like
 
 \section{Discussion}
-Discuss.
+Our proposed featurization for persistence modules is rather naive, but well
+adapted to the use of lattice convolutions as a data processing method. The
+lattice convolutional neural network shows promise as a method for classifying
+features arising from a multiparameter persistence module. The algebraic
+perspective on partially ordered sets, exemplified by lattices, may also offer
+approaches to featurizing more complex invariants of persistence modules. In
+particular, the incidence algebra may offer a natural way to represent the rank
+invariant~\cite{carlsson_theory_2009} in a way amenable to convolution-like
+operations.
+
+We hope with these brief experiments to inspire further work on featurizing
+multidimensional persistence for use in machine learning algorithms.
+% anything else?
 

### 2020-10-10 paper/paper.tex
minor edits

--- 2020-10-09 paper/paper.tex
@@
 $\beta_i(\mathbb{X}) = \dim(H_i(\mathbb{X}))$.}, and the multi-graded Betti
-numbers have an interpretation in terms of births and deaths~\cite{knudson_refinement_2008}.
+numbers have a geometric interpretation in terms of births and deaths~\cite{knudson_refinement_2008}.
 
@@
 metric spaces. This dataset consists of hundreds of 3-dimensional CAD models
-representing objects from 40 classes. We select two of the classes and sample
+representing objects from 10 classes. We select two of the classes and sample
 points from the 3D models to produce finite metric spaces embedded in $\R^3$.
@@
 
-The pipline thus begins with a 3D model, which is sampled to produce a point
+The pipline thus begins with a 3D polyhedral model, of which $3000$ vertices are sampled to produce a point
 cloud in $\R^3$. This point cloud then produces a bifiltered simplicial complex,
@@
 40$ points, producing lattice-indexed signals given by the Hilbert function and
-the multi-graded Betti numbers. These are then passed to the classifier, which
+the multi-graded Betti numbers $\xi_0, \xi_1, \xi_2$--four features in total. These are then passed to the classifier, which
 produces a class prediction.
@@
 As the filter function on these data sets, we use
-\[\rho_{\text{codense}}(x;k) = \frac{k \diam(\mathcal M)}{\sum_{y \in N_k(x)}
+\[\rho_{\text{codense}}(x;k) = \frac{1}{\frac{1}{k} \sum_{y \in N_k(x)}
     d(x,y)},\]

### 2020-10-10 paper/paper.tex

--- 2020-10-10 paper/paper.tex
@@
 40$ points, producing lattice-indexed signals given by the Hilbert function and
-the multi-graded Betti numbers. These are then passed to the classifier, which
+the multi-graded Betti numbers $\xi_0, \xi_1, \xi_2$--four features in total. These are then passed to the classifier, which
 produces a class prediction, in this case either ``sofa'' or ``monitor.''

### 2020-10-10 paper/paper.tex
added figures final edits/cuts

@@
 \usepackage{mymacros}
+\usepackage{graphicx}
 
@@
 persistent homology, see~\cite{lesnick_interactive_2015}. An introduction to
-lattices may be found in~\cite{}.
+lattices may be found in~\cite{davey2002introduction}.
 
@@
 simplicial complexes given by
-\[\mathbb{X}_{r,t} = \text{Rips}_r{x \in \mathcal M \mid \rho(x) \leq t}.\]
+\[\mathbb{X}_{r,t} = \text{Rips}_r\{x \in \mathcal M \mid \rho(x) \leq t\}.\]
 There is a natural inclusion $\mathbb{X}_{r,t} \hookrightarrow
@@
 \times [n] \to \R^{N_{\text{out}}\times N_{\text{in}}}$. If we label the
-entries of $f(x,y)$ by $f_i$ and the entries of $g(x,y)$ by $g^i_j$ The layer then acts by
+entries of $f(x,y)$ by $f_i$ and the entries of $g(x,y)$ by $g^i_j$, the layer then acts by
 \[\text{MeetConv}(f)(x,y)^j = \sum_{i} (f_i \ast_{\wedge} g^i_j)(x,y) = \sum_i
@@
 \section{Experiments}
-\begin{figure}
+\begin{figure}[b]
   \caption{Comparison training curves for the lattice neural network and
     standard convolutional neural network.}\label{fig:comparison}
+    \begin{center}
+    \includegraphics[width=0.49\textwidth]{lattice_accuracy.png}
+    \vspace{0.2cm}
+    \includegraphics[width=0.49\textwidth]{conv_accuracy.png}
+    \end{center}
+
 \end{figure}
@@
 similarly on the training set. However, the lattice convolution network's
-predictions generalize more accurately to the testing set.
+predictions generalize more accurately to the testing set ($\approx 7\%$ improvement in testing accuracy).
+This improvement is  at the expense of noisy training as well as dramatically increased training time.  
 %% more discussion of what the data actually looks like

### 2020-10-10 paper/paper.tex
reduce to page limit

@@
 
-Due to space constraints, we can offer only a brief overview of multiparameter
-persistent homology. For a primer on persistent homology,
-see~\cite{ghrist_barcodes:_2008, carlsson_topology_2009}; for multiparameter
-persistent homology, see~\cite{lesnick_interactive_2015}. An introduction to
-lattices may be found in~\cite{davey2002introduction}.
+Space constraints require that this section be laconic. For a primer on
+persistent homology, see~\cite{ghrist_barcodes:_2008, carlsson_topology_2009};
+for multiparameter persistent homology, see~\cite{lesnick_interactive_2015}. An
+introduction to lattices may be found in~\cite{davey2002introduction}.
 
@@
 
-This representation theoretic fact gives a representation\footnote{Pun intended.} of
-$\R$-indexed persistence modules via \introduce{barcodes} or
-\introduce{persistence diagrams}. Each bar $I_{[a,b)}$ in the barcode represents
-a homology class which is \introduce{born} at $a$ and \introduce{dies} at $b$.
+% This representation theoretic fact gives a representation\footnote{Pun intended.} of
+% $\R$-indexed persistence modules via \introduce{barcodes} or
+% \introduce{persistence diagrams}. Each bar $I_{[a,b)}$ in the barcode represents
+% a homology class which is \introduce{born} at $a$ and \introduce{dies} at $b$.
 
@@
 1$) of the complex $\mathbb{X}_{r,t}$ at each $(r,t) \in R_+\times \R$. The multi-graded
-Betti numbers, on the other hand, capture information about locations of births
-and deaths of persistence classes.
+Betti numbers, on the other hand, capture information about births
+and deaths of homology classes.
 
@@
 and their properties produce an algebraic characterization of lattices; the
-order theoretic and algebraic properties of a lattice can be recovered from each
-other. The key insight of~\cite{pueschel_discrete_2019} is that the meet and
+ordering can be recovered from the algebra and vice versa. The key insight of~\cite{pueschel_discrete_2019} is that the meet and
 join operations on a lattice define two ``shift operators'' that can be
@@
 
-A particularly nice class of examples of lattices are given by the sets $\R^n$
+A nice class of examples of lattices are given by the sets $\R^n$
 viewed as partially ordered sets, with the ordering $(x_1,\ldots,x_n) \leq
@@
 of course, the indexing sets for persistent homology, suggesting that lattice
-convolutions over $\R^n$ or its finite sublattices may be useful in analyzing
+convolutions over $\R^n$ or its finite sublattices may be useful in processing
 data coming from multiparameter persistence computations.
@@
   \caption{Comparison training curves for the lattice neural network and
-    standard convolutional neural network.}\label{fig:comparison}
+    standard convolutional neural network. Results are averaged over 10 runs.}\label{fig:comparison}
     \begin{center}
@@
 
-As the filter function on these data sets, we use
+As the filter function on these data sets, we use the \introduce{codensity} function
 \[\rho_{\text{codense}}(x;k) = \frac{1}{\frac{1}{k} \sum_{y \in N_k(x)}
     d(x,y)},\]
-where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$. This is the
-\introduce{codensity} filtration, so named because the points in the densest
-regions of $\mathcal M$ will appear first.
+where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$.
+
+% This is the
+% \introduce{codensity} filtration, so named because the points in the densest
+% regions of $\mathcal M$ will appear first.
 
@@
 predictions generalize more accurately to the testing set ($\approx 7\%$ improvement in testing accuracy).
-This improvement is  at the expense of noisy training as well as dramatically increased training time.  
+This improvement is  at the expense of more variability in performance during
+training. %noisy training as well as dramatically increased training time.  
 %% more discussion of what the data actually looks like
@@
 operations.
-
 We hope with these brief experiments to inspire further work on featurizing

### 2020-10-10 paper/paper.tex
submitted

@@
 % to avoid loading the natbib package, add option nonatbib:
-\usepackage[nonatbib]{neurips_2020_tda}
+\usepackage[preprint]{neurips_2020_tda}
 
@@
 There are various algebraic invariants; in this paper we will use the
-\textit{Hilbert function} and the \textit{multi-graded Betti numbers}, both of
+\textit{Hilbert function} and the \textit{multi-graded Betti numbers}\footnote{\textit{Caveat lector:} the multi-graded (algebraic) Betti numbers need not be confused with the topological Betti numbers, i.e.~the rank of homology.}, both of
 which are $\mathbb{N}$-valued functions on the parameter space.
@@
 The Hilbert function is nothing more than the pointwise
-(topological) Betti numbers\footnote{\textit{Caveat lector:} the multi-graded
-Betti numbers are not the same as the topological Betti numbers
-$\beta_i(\mathbb{X}) = \dim(H_i(\mathbb{X}))$.}, and the multi-graded Betti
+(topological) Betti numbers, and the multi-graded Betti
 numbers have a geometric interpretation in terms of births and deaths~\cite{knudson_refinement_2008}.
@@
 \text{Rips}_{r'}(\mathcal M)$ induce maps $PH_i(r) \to PH_i(r')$, producing the
-data of \introduce{persistence module}. This structure can be compactly
+data of a \introduce{persistence module}. This structure can be compactly
 described as a functor from $\R$, viewed as a category via its standard order
@@
 There is a natural inclusion $\mathbb{X}_{r,t} \hookrightarrow
-\mathbb{X}_{r',t'}$ whenever $(r,t) \leq (r',t')$ in the lattice $\R \times R$.
+\mathbb{X}_{r',t'}$ whenever $(r,t) \leq (r',t')$ in the lattice $\R \times \R$.
 Composing with the homology functor produces a 2-parameter persistence module
@@
 
-While there does not exist a discrete set of invariants for $M$, we can extract
+While there does not exist a discrete set of invariants for  $PH_i$, we can extract
 meaningful features. Two particularly informative types of features are 
  the \introduce{Hilbert function}
-  \[\text{Hilb}: R_+ \times R \to \Z_+;\quad \mathbf{x} \mapsto \dim(M_\mathbf{x}),\] and
+  \[\text{Hilb}: \R_+ \times \R \to \Z_+;\quad \mathbf{x} \mapsto \dim(M_\mathbf{x}),\] and
 the \introduce{multi-graded Betti numbers} $\xi_j: L \to \Z_+$, for $j =
-0,1,2$. For $M = PH_i$ as above, the Hilbert function counts the number of
+0,1,2$. For $PH_i$ as above, the Hilbert function counts the number of
 connected components ($i=0$), cycles ($i=1$), or higher dimensional voids ($i >
-1$) of the complex $\mathbb{X}_{r,t}$ at each $(r,t) \in R_+\times \R$. The multi-graded
+1$) of the complex $\mathbb{X}_{r,t}$ at each $(r,t) \in \R_+\times \R$. The multi-graded
 Betti numbers, on the other hand, capture information about births
@@
 
-Classical signal processing proceeds by constructing filters for space- or
-time-indexed signals using convolutional operators. These implicitly rely on the
+Classical signal processing proceeds by constructing filters for space- or time-indexed signals using convolutional operators. These implicitly rely on the
 algebraic properties of the underlying space, in particular the existence of
@@
 of an abelian group. Rather, with its partial order structure, the indexing set
-is a lattice. In processing signals associated with the persistence module, it
+is a lattice. In processing signals associated with a persistence module, it
 may be useful to take this structure into account rather than imposing the
@@
 \section{Experiments}
-\begin{figure}[b]
-  \caption{Comparison training curves for the lattice neural network and
-    standard convolutional neural network. Results are averaged over 10 runs.}\label{fig:comparison}
-    \begin{center}
-    \includegraphics[width=0.49\textwidth]{lattice_accuracy.png}
-    \vspace{0.2cm}
-    \includegraphics[width=0.49\textwidth]{conv_accuracy.png}
-    \end{center}
-
-\end{figure}
-
 We use a small portion of the Princeton ModelNet
@@
 40$ points, producing lattice-indexed signals given by the Hilbert function and
-the multi-graded Betti numbers $\xi_0, \xi_1, \xi_2$--four features in total. These are then passed to the classifier, which
+the multi-graded Betti numbers $\xi_0, \xi_1, \xi_2$; four features in total. These are then passed to the classifier, which
 produces a class prediction, in this case either ``sofa'' or ``monitor.''
 
-As the filter function on these data sets, we use the \introduce{codensity} function
-\[\rho_{\text{codense}}(x;k) = \frac{1}{\frac{1}{k} \sum_{y \in N_k(x)}
-    d(x,y)},\]
-where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$.
+As the filter function on these data sets, we use the \introduce{codensity} function, $\rho_{\text{codense}}(x;k) = \left( \frac{1}{k} \sum_{y \in N_k(x)} d(x,y) \right)^{-1}$,
+where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$; we select $k=100$.
 
@@
 The fully connected layers have 32 features at each inner layer.
+We use a cross entropy loss function with a softmax in the final layer.
 The networks are trained using the Adam gradient algorithm with learning rate
@@
 This improvement is  at the expense of more variability in performance during
-training. %noisy training as well as dramatically increased training time.  
-%% more discussion of what the data actually looks like
+training. (Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv} .)
 
+\begin{figure}[h]
+  \caption{Comparison training curves for the lattice neural network and
+    standard convolutional neural network. Results are averaged over 5 runs.}\label{fig:comparison}
+    \begin{center}
+%    \includegraphics[width=0.49\textwidth]{testing-accuracy.png}
+%    \vspace{0.2cm}
+%    \includegraphics[width=0.49\textwidth]{training-accuracy.png}
+	\includegraphics[width=0.85\textwidth]{figure.png}
+    \end{center}
+\end{figure}
 \section{Discussion}
@@
 
+\newpage
+\small
 \bibliographystyle{plain}

### 2020-10-10 code/rivet_get_features.py

@@ -46,20 +46,4 @@ for category in os.listdir(main_path):
         for deg in range(1):
             output_name = '/home/ubuntu/code/invariants/testing_'+str(category)+ "_h"+ str(deg)+"_"+str(index)+".txt"
             rivet_find_invariants(name,output_name,deg,x_bins,y_bins)
-#----------------------------------------------------------------------------------------------------------------------
-data_path = "/home/ubuntu/code/data/ModelNet10/ModelNet10/"
-label_dict = {}
-for index,category in enumerate(os.listdir(data_path)):
-    v = torch.zeros(len(os.listdir(data_path)))
-    v[index] = 1.0
-    label_dict[category] = v
-
-path = '/home/ubuntu/code/invariants/'
-N = len(os.listdir(path))
-X = torch.empty(N,4,x_bins,y_bins)
-Y = torch.empty(N,10)
-for index,file_name in enumerate(os.listdir('/home/ubuntu/code/invariants/')):
-    X[index,:,:,:] = parse_rivet_output(file_name,x_bins,y_bins)
-    v = label_dict[filename.split('_')[1]]
-    Y[index,:] = v
 

### 2020-10-10 code/training_conv.py

@@ -99,16 +99,3 @@ for trial in range(n_trials):
         test_accuracy[epoch,trial] = correct/total
 torch.save(train_accuracy,'./conv_train_accuracy.pt')
 torch.save(test_accuracy,'./conv_test_accuracy.pt')
-
-mean_train_accuracy = torch.mean(train_accuracy,dim=1).cpu()
-mean_test_accuracy = torch.mean(test_accuracy,dim=1).cpu()
-
-
-figure(figsize=(10,10))
-xlabel('Epochs')
-ylabel('Accuracy')
-plot(mean_train_accuracy,'g',label='Training')
-plot(mean_test_accuracy,'b',label='Testing')
-title('Cassification accuracy: ConvClassifier')
-legend()
-savefig('conv_accuracy.png',dpi=300)

### 2020-11-19 paper/paper.tex
minor edits to paper from reviewer comment

@@
 % to avoid loading the natbib package, add option nonatbib:
-\usepackage[preprint]{neurips_2020_tda}
+\usepackage[final]{neurips_2020_tda}
 
@@
   Hans Riess \\
-  Department of Electrical and Systems Engineering \\
   University of Pennsylvania\\
-  Philadelphia, PA 19104 \\
   \texttt{hmr@seas.upenn.edu} \\
@@
   Jakob Hansen \\
-  Department of Mathematics \\
   Ohio State University \\
-  Columbus, OH 43210 \\
   \texttt{hansen.612@osu.edu}
@@
 numbers have a geometric interpretation in terms of births and deaths~\cite{knudson_refinement_2008}.
-
-% The \textit{rank
-% invariant}, another invariant, is shown to be complete in the case of single
-% dimensional persistence \cite{carlsson_theory_2009}; due to its difficulty to
-% compute it is not considered here.
+ The \textit{rank
+ invariant}, another invariant, is shown to be complete in the case of single
+ dimensional persistence \cite{carlsson_theory_2009}; due to its difficulty to
+ compute it is not considered here.
 
@@
 Second, %for all the attention multidimensional persistence has received,
-there has been no activity, as far as the authors are aware, studying the extraction
-of suitable features for multidimensional persistent homology.
+there has been only very recent and preliminary activity \cite{vipond2020multiparameter,carriere2020multiparameter} focusing on extraction
+of suitable features for multidimensional persistent homology. A full-fledged deep learning pipeline
+for multidimensional persistence waits in the wings.
 %Carlsson has a little bit in a recent paper...
 
-We hope to ignite an interest in filling both of these gaps. In this paper, we
+We hope to ignite further interest in filling both of these gaps. In this paper, we
 propose a naive featurization of multidimensional persistence modules based on
@@
 convolutional architecture.
+
+\subsection*{Related work}
+
+Very recent advances have been made to featurize multidimensional persistence modules via
+landscapes \cite{vipond2020multiparameter} and images \cite{carriere2020multiparameter}.
+Our naive approach at featurizing $2$-dimensional persistence modules has the advantage
+of being readily computable with existing software \cite{lesnick_interactive_2015}.
+Persistence modules supported on lattices are of increased interest.
+By leveraging M\"{o}bius inversion, these persistence modules are shown to generate a stable persistence diagram \cite{mccleary2020edit} as well as factor through a nice category with pseudo-inverses \cite{krishnan2020invertibility}.
 
@@
 identity where possible and the zero map otherwise.
-% is this the right shape for the intervals?
 
-% This representation theoretic fact gives a representation\footnote{Pun intended.} of
-% $\R$-indexed persistence modules via \introduce{barcodes} or
-% \introduce{persistence diagrams}. Each bar $I_{[a,b)}$ in the barcode represents
-% a homology class which is \introduce{born} at $a$ and \introduce{dies} at $b$.
+%This representation theoretic fact gives a representation (\textit{no pun intended}) of
+%$\R$-indexed persistence modules via \introduce{barcodes} or
+%\introduce{persistence diagrams}. Each bar $I_{[a,b)}$ in the barcode represents
+%a homology class which is \introduce{born} at $a$ and \introduce{dies} at $b$.
 
@@
 
-While there does not exist a discrete set of invariants for  $PH_i$, we can extract
+While there does not exist a complete discrete invariant for  $PH_i$, we can extract
 meaningful features. Two particularly informative types of features are 
  the \introduce{Hilbert function}
-  \[\text{Hilb}: \R_+ \times \R \to \Z_+;\quad \mathbf{x} \mapsto \dim(M_\mathbf{x}),\] and
-the \introduce{multi-graded Betti numbers} $\xi_j: L \to \Z_+$, for $j =
+  \[\text{Hilb}: \R_+ \times \R \to \Z_+;\quad (r,t) \mapsto \dim(PH_i(r,t)),\] and
+the \introduce{multi-graded Betti numbers} $\xi_j: \R_+ \times \R \to \Z_+$, for $j =
 0,1,2$. For $PH_i$ as above, the Hilbert function counts the number of
@@
 Betti numbers, on the other hand, capture information about births
-and deaths of homology classes.
+and deaths of homology classes.\footnote{ $\xi_j(r,t)$ counts the rank of the $j$th term of the free resolution of $PH_i$ at grading $(r,t)$ \cite{lesnick_interactive_2015}.}
 
@@
 
-Convolutional neural networks are uesful in part because the convolution kernels
+Convolutional neural networks are useful in part because the convolution kernels
 (here the functions $g$) can have very small support, reducing the number of
@@
 cloud in $\R^3$. This point cloud then produces a bifiltered simplicial complex,
-whose persistent homology we calculate using
+whose persistent homology in degree zero we calculate using
 RIVET~\cite{lesnick_interactive_2015}, sampled at a discrete grid of $40 \times
@@
 We use a cross entropy loss function with a softmax in the final layer.
-The networks are trained using the Adam gradient algorithm with learning rate
-$0.001$ for 50 epochs. We reserve 10\% of the data for testing. Results are
+The networks are trained using the Adam gradient algorithm with weight decay with learning rate
+$5 \cdot 10^{-4}$ for 50 epochs. We reserve 10\% of the data for testing. Results are
 shown in Figure~\ref{fig:comparison}.
@@
 This improvement is  at the expense of more variability in performance during
-training. (Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv} .)
+training.
+%(Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv}.)
 
@@
   \caption{Comparison training curves for the lattice neural network and
-    standard convolutional neural network. Results are averaged over 5 runs.}\label{fig:comparison}
+    standard convolutional neural network.}\label{fig:comparison}
     \begin{center}
@@
 %    \includegraphics[width=0.49\textwidth]{training-accuracy.png}
-	\includegraphics[width=0.85\textwidth]{figure.png}
+%	\includegraphics[width=0.85\textwidth]{figure.png}
     \end{center}

### 2020-11-25 paper/paper.tex
small revisions

--- 2020-10-10 paper/paper.tex
@@
 
-Convolutional neural networks are uesful in part because the convolution kernels
-(here the functions $g$) can have very small support, reducing the number of
-parameters that must be learned. In the standard convolutional setting, these
-kernels are implicitly supported in a neighborhood of the origin, but the
-location of the kernel is not usually explicitly specified. In the lattice
-setting, we do need to specify where the kernel resides. In the abelian group
-case, the kernel is supported near the identity, and similarly, 
-when we treat our domain as a lattice, the kernel should be supported
-near the neutral element of the operation. That is, for a meet convolution, $g$
-should have support near the maximum $(m,n)$, and for a join convolution, $g$
-should have support near the minimum $(0,0)$.
+Traditional convolutional neural networks are useful in part because the
+convolution kernels (here the functions $g$) can have very small support,
+reducing the number of parameters that must be learned. In the standard
+convolutional setting, these kernels are implicitly supported in a neighborhood
+of the origin, but the location of the kernel is not usually explicitly
+specified. In the lattice setting, we do need to specify where the kernel
+resides. In the abelian group case, the kernel is supported near the identity,
+and similarly, when we treat our domain as a lattice, the kernel should be
+supported near the neutral element of the operation. That is, for a meet
+convolution, $g$ should be supported at the maximum $(m,n)$, and for a join
+convolution, $g$ should be supported at the minimum $(0,0)$. This ensures that
+the convolution operators are capable of preserving information at every point
+of the space. For instance, if $g(0,0) \neq 0$, then $(f \ast_{\vee} g)(x,y)$ is
+a sum of terms including $f(x,y)g(0,0)$, so all information from one layer can
+be passed to the next layer.
 
@@
 
-The pipline thus begins with a 3D polyhedral model, of which $3000$ vertices are sampled to produce a point
-cloud in $\R^3$. This point cloud then produces a bifiltered simplicial complex,
-whose persistent homology we calculate using
-RIVET~\cite{lesnick_interactive_2015}, sampled at a discrete grid of $40 \times
-40$ points, producing lattice-indexed signals given by the Hilbert function and
-the multi-graded Betti numbers $\xi_0, \xi_1, \xi_2$; four features in total. These are then passed to the classifier, which
-produces a class prediction, in this case either ``sofa'' or ``monitor.''
+The pipline thus begins with a 3D polyhedral model, of which $3000$ vertices are
+sampled to produce a point cloud in $\R^3$. This point cloud then produces a
+bifiltered simplicial complex, whose degree-$0$ persistent homology we calculate
+using RIVET~\cite{lesnick_interactive_2015}, sampled at a discrete grid of $40
+\times 40$ points, producing lattice-indexed signals given by the Hilbert
+function and the multi-graded Betti numbers $\xi_0, \xi_1, \xi_2$; four features
+in total. These are then passed to the classifier, which produces a class
+prediction, in this case either ``sofa'' or ``monitor.''
 
-As the filter function on these data sets, we use the \introduce{codensity} function, $\rho_{\text{codense}}(x;k) = \left( \frac{1}{k} \sum_{y \in N_k(x)} d(x,y) \right)^{-1}$,
-where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$; we select $k=100$.
-
-% This is the
-% \introduce{codensity} filtration, so named because the points in the densest
-% regions of $\mathcal M$ will appear first.
-
-% A folk theorem is that the
-% two-parameter persistent homology of a Rips/codensity bifiltration is stable
-% under non-Hausdorff perturbations: \textit{the (Rips) persistent homology of a
-%   point sample and another obtained by adding a small number of points at random
-% are close with respect to the interleaving distance}.
+As the filter function on these data sets, we use the \introduce{codensity} function \[\rho_{\text{codense}}(x;k) = \left( \frac{1}{k} \sum_{y \in N_k(x)} d(x,y) \right)^{-1},\]
+where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$; we select
+$k=100$. The name codensity is appropriate because the points in the densest
+regions of $\mathcal M$ appear earlier in the filtration. A folk theorem is that
+the two-parameter persistent homology of a Rips/codensity bifiltration is stable
+under non-Hausdorff perturbations: \textit{the (Rips) persistent homology of a
+point sample and another obtained by adding a small number of points at random
+are close with respect to the interleaving distance}.
 
@@
 Each has three convolutional layers followed by three fully connected layers.
-The lattice-based convolution layers are of the form $\text{MeetConv}(x) +
-\text{JoinConv}(x)$. All convolution kernels have dimension $4 \times 4$, hidden
-convolution layers have 16 features, and the final convolution has 8 features.
-The fully connected layers have 32 features at each inner layer.
-We use a cross entropy loss function with a softmax in the final layer.
-The networks are trained using the Adam gradient algorithm with learning rate
-$0.001$ for 50 epochs. We reserve 10\% of the data for testing. Results are
-shown in Figure~\ref{fig:comparison}.
+The lattice-based convolution layers are of the form $\alpha\text{MeetConv}(x) +
+(1-\alpha)\text{JoinConv}(x)$ for a hyperparameter $\alpha \in [0,1]$. All
+convolution kernels have dimension $4 \times 4$, hidden convolution layers have
+16 features, and the final convolution has 8 features. The fully connected
+layers have 32 features at each inner layer. We use a cross entropy loss
+function with a softmax in the final layer. The networks are trained using the
+Adam gradient algorithm with learning rate $0.001$ for 50 epochs. We reserve
+10\% of the data for testing. Results are shown in Figure~\ref{fig:comparison}.
 
-The lattice-based convolution and classical convolution networks perform
-similarly on the training set. However, the lattice convolution network's
-predictions generalize more accurately to the testing set ($\approx 7\%$ improvement in testing accuracy).
-This improvement is  at the expense of more variability in performance during
-training. (Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv} .)
+% The lattice-based convolution and classical convolution networks perform
+% similarly on the training set. However, the lattice convolution network's
+% predictions generalize more accurately to the testing set ($\approx 7\%$ improvement in testing accuracy).
+% This improvement is  at the expense of more variability in performance during
+% training. (Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv} .)
 
@@
 multidimensional persistence for use in machine learning algorithms.
-% anything else?
 

### 2020-11-25 paper/paper.tex

@@
 be passed to the next layer. 
-
 \section{Experiments}
@@
 % training. (Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv} .)
-
 \begin{figure}[h]
   \caption{Comparison training curves for the lattice neural network and
-    standard convolutional neural network. Results are averaged over 5 runs.}\label{fig:comparison}
+    standard convolutional neural network.}\label{fig:comparison}
     \begin{center}

### 2020-11-26 paper/paper.tex
minor edits new figs

@@
 
-\subsection*{Related work}
-
+\paragraph{Related work}
 Very recent advances have been made to featurize multidimensional persistence modules via
@@
 Persistence modules supported on lattices are of increased interest.
-By leveraging M\"{o}bius inversion, these persistence modules are shown to generate a stable persistence diagram \cite{mccleary2020edit} as well as factor through a nice category with pseudo-inverses \cite{krishnan2020invertibility}.
+By leveraging M\"{o}bius inversion, these persistence modules are shown to generate a stable persistence diagram \cite{mccleary2020edit} as well as factor through a convenient category with pseudo-inverses \cite{krishnan2020invertibility}.
 
@@
 
+\paragraph{Remark}
 Traditional convolutional neural networks are useful in part because the
@@
 \section{Experiments}
-We use a small portion of the Princeton ModelNet
+We use a large portion of the Princeton ModelNet
 dataset~\cite{zhirong_wu_3d_2015} as a source of finite
@@
 in total. These are then passed to the classifier, which produces a class
-prediction, in this case either ``sofa'' or ``monitor.''
+prediction, in this case one of 10 possible household objects.
 
@@
 where $N_k(x)$ is the set of the $k$ nearest neighbors to $x$; we select
-$k=100$. The name codensity is appropriate because the points in the densest
+$k=100$.
+\paragraph{Remark}
+The name codensity is appropriate because the points in the densest
 regions of $\mathcal M$ appear earlier in the filtration. A folk theorem is that
-the two-parameter persistent homology of a Rips/codensity bifiltration is stable
-under non-Hausdorff perturbations: \textit{the (Rips) persistent homology of a
-point sample and another obtained by adding a small number of points at random
-are close with respect to the interleaving distance}.
+the 2-parameter persistent homology of a Rips/codensity bifiltration is stable (w.r.t.~interleaving distance)
+under non-Hausdorff noise (e.g. adding or removing a small number of point samples).
+%: \textit{the (Rips) persistent homology of a
+%point sample and another obtained by adding a (relatively) small number of points at random
+%are close with respect to the interleaving distance}.
 
@@
 Section~\ref{sec:latticeCNN}, and the other uses standard convolutional layers.
-Each has three convolutional layers followed by three fully connected layers.
-The lattice-based convolution layers are of the form $\alpha\text{MeetConv}(x) +
-(1-\alpha)\text{JoinConv}(x)$ for a hyperparameter $\alpha \in [0,1]$. All
+Each has three convolutional layers followed by two fully connected layers.
+The lattice-based convolution layers are of the form $\alpha \cdot \text{MeetConv}(x) +
+(1-\alpha)\cdot\text{JoinConv}(x)$ for a hyperparameter $\alpha \in [0,1]$. All
 convolution kernels have dimension $4 \times 4$, hidden convolution layers have
-16 features, and the final convolution has 8 features. The fully connected
-layers have 32 features at each inner layer. We use a cross entropy loss
-function with a softmax in the final layer. The networks are trained using the
-Adam gradient algorithm with learning rate $0.001$ for 50 epochs. We reserve
+16 features, and the final convolution layer has 8 features. The first two convolution
+layers are followed by max-pooling layers with a $2 \times 2$ kernel.
+The inner fully connected layer has 32 features. We use a cross entropy loss
+function with a softmax in the final layer. The lattice-based convolutional architecture
+is summarized in Figure~\ref{fig:architecture}.
+The networks are trained using the
+Adam gradient algorithm with learning rate $10^{-4}$ for 300 epochs. We reserve
 10\% of the data for testing. Results are shown in Figure~\ref{fig:comparison}.
@@
 % training. (Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv} .)
-\begin{figure}[h]
-  \caption{Comparison training curves for the lattice neural network and
-    standard convolutional neural network.}\label{fig:comparison}
-    \begin{center}
-%    \includegraphics[width=0.49\textwidth]{testing-accuracy.png}
-%    \vspace{0.2cm}
-%    \includegraphics[width=0.49\textwidth]{training-accuracy.png}
-%	\includegraphics[width=0.85\textwidth]{figure.png}
-    \end{center}
-\end{figure}
+
 \section{Discussion}
+
 Our proposed featurization for persistence modules is rather naive, but well
@@
 
-\newpage
+\begin{figure}[h!]
+  \caption{The architecture of our lattice-based convolutional neural network.}\label{fig:architecture}
+    \begin{center}
+    \includegraphics[width=0.75\textwidth]{nn.jpg}
+    \end{center}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Comparison learning curves for the lattice neural network and
+    standard convolutional neural network.}\label{fig:comparison}
+    \begin{center}
+    %\includegraphics[width=0.75\textwidth]{training.png}
+    \includegraphics[width=0.9\textwidth]{testing.png}
+    \end{center}
+\end{figure}
+
+\section*{Acknowledgments}
+The authors would like to thank Chris Wendler for replicating our original experiment.
+We would like to thank the reviewers for providing helpful feedback.
+The author [HR] is partially supported by Office of Naval Research (Grant No.
+N00014-1442-16-1-2010).
 \small

### 2020-11-28 paper/paper.tex
update information about simulations, new plot

@@
 a sum of terms including $f(x,y)g(0,0)$, so all information from one layer can
-be passed to the next layer. 
+be passed to the next layer. A bit more is necessary to avoid degenerate
+convolutions. A kernel supported in a geometrically small neighborhood of the
+neutral element results in trivial receptive fields for most neurons. For
+example, if $(x,y)$ is greater than the maximal element of the support of $g$,
+$(f \ast_{\vee} g)(x,y)$ is simply a scalar multiple of $f(x,y)$. As a result,
+we hypothesize that the appropriate support sets for lattice-convolutional kernels
+are evenly-spaced sublattices including both $(0,0)$ and $(m,n)$.
+
 \section{Experiments}
-We use a large portion of the Princeton ModelNet
+We use a portion of the Princeton ModelNet
 dataset~\cite{zhirong_wu_3d_2015} as a source of finite
 metric spaces. This dataset consists of hundreds of 3-dimensional CAD models
-representing objects from 10 classes. We select two of the classes and sample
+representing objects from 10 classes. We sample
 points from the 3D models to produce finite metric spaces embedded in $\R^3$.
@@
 The lattice-based convolution layers are of the form $\alpha \cdot \text{MeetConv}(x) +
-(1-\alpha)\cdot\text{JoinConv}(x)$ for a hyperparameter $\alpha \in [0,1]$. All
+(1-\alpha)\cdot\text{JoinConv}(x)$ for a hyperparameter $\alpha \in [0,1]$. We
+set $\alpha = \frac{1}{2}$. All
 convolution kernels have dimension $4 \times 4$, hidden convolution layers have
 16 features, and the final convolution layer has 8 features. The first two convolution
-layers are followed by max-pooling layers with a $2 \times 2$ kernel.
+layers are followed by max-pooling layers with a $2 \times 2$ kernel. For the
+lattice convolutional layers, the support of the kernel lay in an evenly spaced
+$4 \times 4$ grid of points in $[m]\times [n]$, while the standard convolutional
+layers had a traditional contiguously supported kernel.
 The inner fully connected layer has 32 features. We use a cross entropy loss
@@
 The networks are trained using the
-Adam gradient algorithm with learning rate $10^{-4}$ for 300 epochs. We reserve
+Adam gradient algorithm with learning rate $2 \times 10^{-4}$ for 300 epochs. We reserve
 10\% of the data for testing. Results are shown in Figure~\ref{fig:comparison}.
@@
 % training. (Our code is available at \texttt{https://github.com/alfred-tarski/latticeconv} .)
+
+The lattice convolutional network slightly underperforms the standard
+convolutional classifier. This is somewhat disappointing, and perhaps indicates
+that the relevant information encoded in degree-0 persistent homology is best
+captured with a geometric notion of locality in $\R^2$.\footnote{Due to a coding
+  error, an earlier version of this paper gave results incorrectly showing the
+  lattice convolutional network outperforming the traditional network.} This
+work has not exhausted the possibilities for lattice convolutions in
+multidimensional persistence, but does suggest circumspection in evaluating
+their future use.
 
@@
     %\includegraphics[width=0.75\textwidth]{training.png}
-    \includegraphics[width=0.9\textwidth]{testing.png}
+      \includegraphics[width=\textwidth]{test_results_2.png}
     \end{center}
@@
 \section*{Acknowledgments}
-The authors would like to thank Chris Wendler for replicating our original experiment.
-We would like to thank the reviewers for providing helpful feedback.
+The authors would like to thank Chris Wendler for replicating our original
+experiment. We would like to thank the reviewers for providing helpful feedback.
 The author [HR] is partially supported by Office of Naval Research (Grant No.
-N00014-1442-16-1-2010).
+N00014-1442-16-1-2010), and the author [JH] is supported by the National Science
+Foundation (NSF-DMS \#1547357).
 \small
